### 2018-11-30 article/article_1.tex
ordenando

\documentclass[review]{elsarticle}
\usepackage{comment}
\usepackage{url}
%
\usepackage[breaklinks]{hyperref}
\usepackage{breakurl}

\usepackage[ruled]{algorithm2e}

%\usepackage{lineno}
%\modulolinenumbers[5]

\journal{Optics Communications}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
\usepackage{subcaption}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[svgnames]{xcolor} % Enabling colors by their 'svgnames'

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Importancia da frequencia de amostragem no analisis del speckle dinamico}
%\tnotetext[mytitlenote]{Fully documented templates are available in the 
%elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

% Group authors per affiliation:
\author{Fernando Pujaico Rivera}
\author{Roberto Alves Braga Jr.}

\address{University Federal of Lavras, Lavras, Brazil}
\fntext[myfootnote2]{201518201@posgrad.ufla.br}
\fntext[myfootnote1]{robertobraga@deg.ufla.br }
%

\begin{abstract}
In this article we show an analysis 
\end{abstract}

\begin{keyword}
Biospeckle laser \sep 
Biospeckle index \sep 
Biospeckle signal\sep 
Biological activity \sep
Dynamic speckle 
\end{keyword}

\end{frontmatter}

\linenumbers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Dynamic laser speckle is a phenomenon that is 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System description}
\label{sec:description}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical analysis}
\label{sec:analysis}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical results} 
\label{sec:numerical}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

In this work were presented comparisons

\section{Acknowledgment}
We wish to acknowledge the partial financial support for this study provided by the $CAPES$ 
scholarship
$PNPD$ Program, $FAPEMIG$ and $CNPQ$.

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------
\section{Bibliography}
\bibliography{report}   %>>>> bibliography data in report.bib
\bibliographystyle{spiebib}   %>>>> makes bibtex use spiebib.bst

%----------------------------------------------------------------------------------------

\end{document}

### 2018-11-30 mcode-15:15:60/programa.m

@@ -20,9 +20,20 @@ DIRSRC=fullfile(OUTPUT,filesep,'45fps');
 DIRSRC=fullfile(OUTPUT,filesep,'60fps');
 [STD60 MEAN60 AVD60 TIME]=func_dir_std(DIRSRC);
 
+func_programa_plot2(   STD15,MEAN15,AVD15,...
+                       STD30,MEAN30,AVD30,...
+                       STD45,MEAN45,AVD45,...
+                       STD60,MEAN60,AVD60,...
+                       TIME,'dir_FPS_f11_raw','FPS_f11_raw');
+
 func_programa_plot2(   STD15/max(STD15),MEAN15,AVD15/max(AVD15),...
                        STD30/max(STD30),MEAN30,AVD30/max(AVD30),...
                        STD45/max(STD45),MEAN45,AVD45/max(AVD45),...
                        STD60/max(STD60),MEAN60,AVD60/max(AVD60),...
-                       TIME,'FPS_f11','FPS_f11');
+                       TIME,'dir_FPS_f11_norm1','FPS_f11_norm1');
 
+func_programa_plot2(   STD15/mean(MEAN15),MEAN15,AVD15/mean(MEAN15),...
+                       STD30/mean(MEAN30),MEAN30,AVD30/mean(MEAN30),...
+                       STD45/mean(MEAN45),MEAN45,AVD45/mean(MEAN45),...
+                       STD60/mean(MEAN60),MEAN60,AVD60/mean(MEAN60),...
+                       TIME,'dir_FPS_f11_norm2','FPS_f11_norm2');

### 2019-02-24 article/article_1.tex
actualizando

@@
 
-\title{Importancia da frequencia de amostragem no analisis del speckle dinamico}
+\title{Importance of Sampling Frequency in the Dynamic Speckle Analysis}
 %\tnotetext[mytitlenote]{Fully documented templates are available in the 
@@
 % Group authors per affiliation:
-\author{Fernando Pujaico Rivera}
-\author{Roberto Alves Braga Jr.}
+\author{------ ----- -----}
+\author{------ ----- -----}
 
@@
 \begin{abstract}
-In this article we show an analysis 
+In this article, we show as the variation of sampling frequency, 
+in a dynamic speckle analysis, affect the value of some dynamic speckle index, 
+in this case: the absolute value of the differences ($AVD$) index, the temporal 
+speckle standard deviation index and the temporal 
+speckle mean index.
+we show that  the dynamic speckle index value decrease your maximum excursion with 
+the grow of sampling frequency because this affect directly the time integration 
+(exposition time) of camera.
 \end{abstract}
@@
 \begin{keyword}
-Biospeckle laser \sep 
-Biospeckle index \sep 
-Biospeckle signal\sep 
-Biological activity \sep
-Dynamic speckle 
+Frequency sampling \sep
+Dynamic speckle index \sep 
+Dynamic speckle index \sep 
+Dynamic speckle analysis
 \end{keyword}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Numerical analysis}
-\label{sec:analysis}
+\subsection{Exposure time of the camera}
+\label{subsec:expositiontime}
+The acquisition time,  frame per seconds ($fps$) or sampling frequency ($F_s$), 
+in the camera Marlin F-033 will be calculated in the 
+ Table \ref{table:1}, where we can see, the shutter register value ($Shutter$), 
+time base register value ($Base$),
+exposure time ($Exposure$),
+exposure time offset ($Offset$) and
+effective exposure time ($E$); so that 
+\begin{equation}
+Exposure= Shutter \times Base,
+\end{equation}
+\begin{equation}
+\frac{1}{F_s}=E= Exposure + Offset.
+\end{equation}
+Where,  $F_s$ is calculated in relation to the  $E$; being that,
+the $Exposure$ represent the photography integration time and $E$ the effective time
+between photographs.
+\begin{table}[h!]
+\centering
+\begin{tabular}{||c c c c c||} 
+ \hline
+ $Shutter$ &  $Base$ [$\mu s$] & $Offset$ [$\mu s$] & $E$ [$ms$] & $F_s$ [$fps$]\\ [0.5ex] 
+ \hline\hline
+ 3332  & 20  & 12  & 66.652  & 15.003  \\ 
+ 1665  & 20  & 12  & 33.312  & 30.019  \\ 
+ 1110  & 20  & 12  & 22.212  & 45.021  \\ 
+ 832   & 20  & 12  & 16.652  & 60.053  \\ [1ex] 
+ \hline
+\end{tabular}
+\caption{Exposition time and sampling frequency}
+\label{table:1}
+\end{table}
+
+\subsection{Data packages in the ink drying process}
+\label{subsec:data1}
+ This data package analyze a drying ink process, 
+ where images data packages are taken at the times
+ $\{0,$ $1,$ $2,$ $3,$ $4,$ $5,$ $6,$ $7,$ $8,$ $9,$ $10\}$ min. 
+ In each time, the package
+ has 512 images of 147 pixels of height and 166 pixels of width.
+ They were use 4 different sampling frequency to the images in each package,
+ being these frequencies $15$, $30$, $45$ and $60$ hz.
+
+\subsection{Data package of the activity analysis in corn seed}
+\label{subsec:data2}
+ This data package analyze the activity of a corn seed with 3 days of germination. 
+ In this point, 
+ They are taken 4 image data packages with different sampling frequencies to each package,
+ being these frequencies $15$, $30$, $45$ and $60$ hz.
+ Each package has 512 images of 29 pixels of height and 31 pixels of width.
+
+\subsection{Test 1: ink drying process}
+\label{subsec:test1}
+The Fig. \ref{fig:test1} represents the data analysis method, acquired at a 
+sampling frequency of $F_s$, 
+with the characteristic seen in the Section \ref{subsec:data1},
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.55\columnwidth]{test1.eps}
+\caption{Data analysis of the ink drying process test.}
+\label{fig:test1}
+\end{figure}
+where, $P(t)$ is an image data package at the time $t$ minutes.
+The $MEAN$ block represent the calculus of a temporal speckle mean index from 
+the package $P(t)$, returning the value $MEAN(t)$, as exposed in the Section \ref{sec:mean}. 
+The $AVD$ block represent the calculus of a absolute values of the differences index from 
+the package $P(t)$, returning the value $AVD(t)$, as exposed in the Section \ref{sec:avd}. 
+The $STD$ block represent the calculus of a temporal speckle standard deviation index from 
+the package $P(t)$, returning the value $STD(t)$, as exposed in the Section \ref{sec:std}.
+And finally,
+the block $HPF$ represents a digital finite impulse response ``high-pass filter'' 
+with order $40$ and cut-off at $0.25F_s$ that causes to have the at end of path
+the $STDF(t)$ index value, a frequency filtered version of $STD(t)$.
+According the information of the data packages, 
+we will have indexes values, for each minutes during 10 minutes.
+
+\subsection{Test 2: Activity analysis in corn seed}
+\label{subsec:test2}
+The activity analysis of a corn seed, 
+uses the information of data package seen in the Section \ref{subsec:data1}.
+We analyze this information of similar way to the seen in the Section \ref{subsec:test1},
+with the difference that is taken an data package at the time $t$ (3 days of germination).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Theoretical definitions}
+\label{sec:theoretical}
+
+\subsection{temporal speckle mean index}
+\label{sec:mean}
+
+\subsection{Absolute Values of the Differences (AVD)}
+\label{sec:avd}
+%% Following the working flow in Fig. 2, the randomly-selected points in the ROI were 
+%% analysed, with respect to their behaviour in time, by means of the Absolute Values 
+%% of the Differences (AVD) method [35] using the data in the COM without 
+%% normalization. The AVD method can be expressed by Equation (1):
+
+%% where the COM is the Co-Occurrence Matrix related to the THSP, and the i and j 
+%% variables represent the line i and the column j of each point of the COM matrix.
+
+Frequency composition from $F_s/4$ until $F_s/2$ Hz like as  $HPF$ of first order.
+
+\subsection{Temporal speckle standard deviation index}
+\label{sec:std}
+Frequency composition from $0$ until $F_s/2$ Hz like as  $HPF$ of first order.
+
+\subsection{Filtered temporal speckle standard deviation index}
+\label{sec:stdf}
+Frequency composition from $0$ until $F_s/2$ Hz like as  $HPF$ of first order.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Numerical results} 
-\label{sec:numerical}
+\label{sec:numericalresults}
+
+\subsection{Result of test 1}
+\label{subsec:resulttest1}
+This test shows the analyze result of an ink drying process, across 10 minutes,
+with the sampling frequency: $15$, $30$, $45$ and $60$Hz.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The Figure \ref{fig:MEANtest1} analyze the $MEAN(t)$ index,
+in the test showed in the Section \ref{subsec:test1},
+to each time $t$ for 4 sampling frequencies.
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{FPS_f11_rawMEAN.eps}
+    \caption{$MEAN$ index value.}\label{fig:MEANtest1}
+\end{figure}
+It easy to see as the value of index has a monotonous 
+behavior over time. By other side the values in the curves decreases in proportion with 
+the grow of sampling frequency.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The Figure \ref{fig:AVDtest1} shows the result of analysis explained in the 
+Section \ref{subsec:test1} about the $AVD(t)$ index.
+\begin{figure}[ht!]
+    \centering
+    \begin{subfigure}{0.48\textwidth}
+        \caption{$AVD$ index value.}
+        \includegraphics[width=\textwidth]{FPS_f11_rawAVD.eps}
+        \label{fig:avdraw}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}{0.48\textwidth}
+        \caption{Normalized $AVD$ index value.}
+        \includegraphics[width=\textwidth]{FPS_f11_norm1AVD.eps}
+        \label{fig:avdnorm}
+    \end{subfigure}
+    \caption{$AVD$ index anaysis.}\label{fig:AVDtest1}
+\end{figure}
+The Figure \ref{fig:avdraw} shows the $AVD(t)$ index, in each time $t$, 
+to 4 sampling frequencies, showing a different behavior across time in each sampling frequency,
+so that, the value of the index in all  the curve decreases in proportion with 
+the grow of sampling frequency. By other side,
+the Figure \ref{fig:avdnorm} shows a normalized version of $AVD(t)$ index, 
+so that the maximum value of curves have an unit value; thus,
+It is easy to see that the maximum excursion of the curve is greater when decrease
+the sampling frequency. Remembering that this index use information in a frequency
+band between $F_s/4$ until $F_s/2$ Hz, as seen in Section \ref{sec:avd}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The Figure \ref{fig:STDtest1} analyze the $STD(t)$ index in the test showed in the 
+Section \ref{subsec:test1}.
+\begin{figure}[ht!]
+    \centering
+    \begin{subfigure}{0.48\textwidth}
+        \caption{$STD$ index value.}
+        \includegraphics[width=\textwidth]{FPS_f11_rawSTD.eps}
+        \label{fig:stdraw}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}{0.48\textwidth}
+        \caption{Normalized $STD$ index value.}
+        \includegraphics[width=\textwidth]{FPS_f11_norm1STD.eps}
+        \label{fig:stdnorm}
+    \end{subfigure}
+    \caption{$STD$ index anaysis.}\label{fig:STDtest1}
+\end{figure}
+The Figure \ref{fig:stdraw} shows the  behavior of $STD(t)$ index, in each time $t$, 
+to 4 different sampling frequencies. Remembering that this index uses information in a frequency
+band between $0$ until $F_s/2$ Hz, as seen in Section \ref{sec:std}.
+This index shows a different behavior across time to each sampling frequency,
+so that, the value of the index in each time of curve decreases in proportion with 
+the grow of sampling frequency. By other side,
+the Figure \ref{fig:stdnorm} shows a normalized version of $STD(t)$ index;
+being the unit, the maximum value of curves; thus,
+It is easy to see that exist a small difference between the maximum excursion 
+of the curves with different sampling frequency; even so, It is possible to observe
+a decrease of the maximum excursion in the curve with the grow of the sampling frequency.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The Figure \ref{fig:STDFtest1}, analyze the $STDF(t)$ index, in the test showed in the 
+Section \ref{subsec:test1}.
+\begin{figure}[ht!]
+    \centering
+    \begin{subfigure}{0.48\textwidth}
+        \caption{$STDF$ index value.}
+        \includegraphics[width=\textwidth]{FPS_f11_rawSTDF.eps}
+        \label{fig:stdfraw}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}{0.48\textwidth}
+        \caption{Normalized $STDF$ index value.}
+        \includegraphics[width=\textwidth]{FPS_f11_norm1STDF.eps}
+        \label{fig:stdfnorm}
+    \end{subfigure}
+    \caption{$STDF$ index anaysis.}\label{fig:STDFtest1}
+\end{figure}
+The Figure \ref{fig:stdfraw} shows the behavior $STDF(t)$ index, in each time $t$, 
+to 4 different sampling frequencies. Remembering that this index uses filtered 
+information of datapack, so that your frequency
+band is between $F_s/4$ and $F_s/2$ Hz, of similar way of $AVD(t)$ index but with
+different order filter, as seen in Section \ref{sec:stdf}.
+This index shows monotone decreasing behavior in time, where we observe 
+a different behavior across time to each different sampling frequency;
+so that, the value of the index in each time of curve decreases in proportion with 
+the grow of sampling frequency. By other side,
+the Figure \ref{fig:stdfnorm} shows a normalized version of $STDF(t)$ index;
+being the unit, the maximum value of curves; thus,
+It is easy to see that exist a considerable difference between the maximum excursion 
+of the curves with the use of sampling frequency; so, It is possible to observe a 
+grow of the maximum excursion with the grow of the sampling frequency.
+
+\subsection{Result of test 2}
+\label{subsec:resulttest2}
+
+\section{Analysis results} 
+\label{sec:analysisresults}
+
+\subsection{Analysis of results: test 1}
+\label{subsec:analysistest1}
+In the results of ink drying process test, seen in Section \ref{subsec:resulttest1},
+we can observe in the Figure \ref{fig:MEANtest1}, that the index shows a relation 
+between the value of curve and the sampling frequency of datapack. 
+How is known \cite{Nothdurft:05}, the temporal speckle mean index is related to 
+the observed illumination level in the surface of study material.
+Thus, we can conclude that the level of illumination perceived by the camera decrease
+with the increment of sampling frequency. 
+This is because that the exposition time is modified, see Section \ref{subsec:expositiontime}, 
+with the alteration of sampling frequency, 
+so that less lighting is used to take the picture and consequently the 
+temporal speckle mean index decrease in  your value.
+The modification of exposition time also affect other indexes, 
+how can it be seen in the Figures \ref{fig:AVDtest1}, \ref{fig:STDtest1} and  \ref{fig:STDFtest1}, 
+where these indexes decrease your values in concordance with the decrease of exposition time.
+Other way in that  the sampling frequency affect the values of indexes,
+It is that it limits the band of signal frequency analyzed; for example,
+a sampling frequency $F_s$ causes that the analyzed signal frequency band will be between $0 Hz$ and $F_s/2~Hz$.
+Thus, in this context we have an index as $MEAN(t)$ that use information at  $0~Hz$ only, 
+the index $STD(t)$ that use information between $\langle \left. 0, F_s/2 \right ] Hz$, 
+and be other side we have indexes as the $AVD(t)$ and the $STDF(t)$ index, that use information of half frequency band, 
+this is between $\left [ F_s/4, F_s/2 \right ] Hz$.
+In the comparison between $STD(t)$ vs  $\{$ $STDF(t)$ and $AVD(t)$ $\}$, 
+we can observe how the half part  use of frequency band causes the decrease of curves values, 
+but considerably good values in the maximum excursion of the curve. By other side,
+in the case of ink drying process, the use of complete frequency band, 
+It returns low values of maximum excursion in the curves. 
+The importance of excursion in this test,
+ It is due the necessity of to have significant differences en the values of two states,
+when the sample start or end the ink drying process.
 
@@
 
-In this work were presented comparisons
+In this work were presented comparisons of behavior of three dynamic speckle indexes
+subject to different values of sampling frequency, thus we concluded that:
+It is important to know to choose an appropriate sampling frequency, 
+being recommendable to use the minimal sampling frequency possible to get an acceptable maximum excursion,
+so that the phenomenon under study to be in the analyzed frequency band.
+Finally, 
+we show that the digitization  of speckle signal imply a restriction of frequency 
+band of signal and consequently this affect the result of an speckle analysis.
 

### 2019-02-24 mcode-15-25/func_programa_plot.m

@@ -1,28 +1,0 @@
-function func_programa_plot(STD15,MEAN15,AVD15,STD25,MEAN25,AVD25,TIME,OUTPUT,PRENAME)
-
-mkdir(OUTPUT);
-
-MAXY=max([max(STD15) max(STD25)]);
-plot(TIME,STD15,'-o',TIME,STD25,'-s'), grid
-ylim([0 MAXY*1.1])
-xlabel('Time (min)')
-ylabel('STD')
-legend('15 fps','25 fps');
-print(gcf,fullfile(OUTPUT,filesep,[PRENAME 'STD.png']),'-dpng')
-
-MAXY=max([max(MEAN15) max(MEAN25)]);
-plot(TIME,MEAN15,'-o',TIME,MEAN25,'-s'), grid
-ylim([0 MAXY*1.1])
-xlabel('Time (min)')
-ylabel('MEAN')
-legend('15 fps','25 fps');
-print(gcf,fullfile(OUTPUT,filesep,[PRENAME 'MEAN.png']),'-dpng')
-
-MAXY=max([max(AVD15) max(AVD25)]);
-plot(TIME,AVD15,'-o',TIME,AVD25,'-s'), grid
-ylim([0 MAXY*1.1])
-xlabel('Time (min)')
-ylabel('AVD')
-legend('15 fps','25 fps');
-print(gcf,fullfile(OUTPUT,filesep,[PRENAME 'AVD.png']),'-dpng')
-end

### 2019-02-24 mcode-15:15:60/func_dir_std.m

@@ -1,26 +1,0 @@
-function [STD MEAN AVD TIME]=func_dir_std(DIRROOT,varargin)
-
-    %H=DIRROOT
-    STD=zeros(1,11);
-    MEAN=zeros(1,11);
-    AVD=zeros(1,11);
-    TIME=[0:10];
-    for II=0:10
-        DIR=fullfile(DIRROOT,[num2str(II) 'min'],'ROI');
-
-        %% To filenames: 'img1coffee.bmp', 'img2coffee,bmp', ..., 'img100coffee.bmp'
-        DATA = datapack(DIR,'%d',1,512,'bmp');
-        if(nargin>1)
-            NN=round(size(DATA,3)/varargin{1});
-            ID=1+(0:(NN-1))*varargin{1};
-            DATA=DATA(:,:,ID);
-        endif 
-        [C D E]=stdcont(DATA,'off');
-        GAVD=graphavd(DATA,'off');
-
-        STD(II+1)=mean(mean(D));
-        MEAN(II+1)=mean(mean(E));
-        AVD(II+1)=mean(mean(GAVD));
-    end
-    
-end

### 2019-02-24 mcode-15:15:60/func_programa_plot2.m

@@ -1,32 +1,0 @@
-function func_programa_plot2(   STD15,MEAN15,AVD15,...
-                                STD30,MEAN30,AVD30,...
-                                STD45,MEAN45,AVD45,...
-                                STD60,MEAN60,AVD60,...
-                                TIME,OUTPUT,PRENAME)
-
-mkdir(OUTPUT);
-
-MAXY=max([max(STD15) max(STD30) max(STD45) max(STD60)]);
-plot(TIME,STD15,'-o',TIME,STD30,'-s',TIME,STD45,'-<',TIME,STD60,'-*'), grid
-ylim([0 MAXY*1.1])
-xlabel('Time (min)')
-ylabel('STD')
-legend('15 fps','30 fps','45 fps','60 fps');
-print(gcf,fullfile(OUTPUT,filesep,[PRENAME 'STD.png']),'-dpng')
-
-MAXY=max([max(MEAN15) max(MEAN30) max(MEAN45) max(MEAN60)]);
-plot(TIME,MEAN15,'-o',TIME,MEAN30,'-s',TIME,MEAN45,'-<',TIME,MEAN60,'-*'), grid
-ylim([0 MAXY*1.1])
-xlabel('Time (min)')
-ylabel('MEAN')
-legend('15 fps','30 fps','45 fps','60 fps');
-print(gcf,fullfile(OUTPUT,filesep,[PRENAME 'MEAN.png']),'-dpng')
-
-MAXY=max([max(AVD15) max(AVD30) max(AVD45) max(AVD60)]);
-plot(TIME,AVD15,'-o',TIME,AVD30,'-s',TIME,AVD45,'-<',TIME,AVD60,'-*'), grid
-ylim([0 MAXY*1.1])
-xlabel('Time (min)')
-ylabel('AVD')
-legend('15 fps','30 fps','45 fps','60 fps');
-print(gcf,fullfile(OUTPUT,filesep,[PRENAME 'AVD.png']),'-dpng')
-end

### 2019-02-24 mcode-15:15:60/programa.m

@@ -1,39 +1,0 @@
-%
-
-pkg load bsltl
-
-OUTPUT='/home/fernando/Downloads/ROLANDO/FPS_f11';
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-DIRSRC=fullfile(OUTPUT,filesep,'15fps');
-[STD15 MEAN15 AVD15 TIME]=func_dir_std(DIRSRC);
-
-DIRSRC=fullfile(OUTPUT,filesep,'30fps');
-[STD30 MEAN30 AVD30 TIME]=func_dir_std(DIRSRC);
-
-DIRSRC=fullfile(OUTPUT,filesep,'45fps');
-[STD45 MEAN45 AVD45 TIME]=func_dir_std(DIRSRC);
-
-DIRSRC=fullfile(OUTPUT,filesep,'60fps');
-[STD60 MEAN60 AVD60 TIME]=func_dir_std(DIRSRC);
-
-func_programa_plot2(   STD15,MEAN15,AVD15,...
-                       STD30,MEAN30,AVD30,...
-                       STD45,MEAN45,AVD45,...
-                       STD60,MEAN60,AVD60,...
-                       TIME,'dir_FPS_f11_raw','FPS_f11_raw');
-
-func_programa_plot2(   STD15/max(STD15),MEAN15,AVD15/max(AVD15),...
-                       STD30/max(STD30),MEAN30,AVD30/max(AVD30),...
-                       STD45/max(STD45),MEAN45,AVD45/max(AVD45),...
-                       STD60/max(STD60),MEAN60,AVD60/max(AVD60),...
-                       TIME,'dir_FPS_f11_norm1','FPS_f11_norm1');
-
-func_programa_plot2(   STD15/mean(MEAN15),MEAN15,AVD15/mean(MEAN15),...
-                       STD30/mean(MEAN30),MEAN30,AVD30/mean(MEAN30),...
[…]

### 2019-02-24 mcode/OLD/mcode-freq:15-25/func_programa_plot.m

@@ -1,0 +1,28 @@
+function func_programa_plot(STD15,MEAN15,AVD15,STD25,MEAN25,AVD25,TIME,OUTPUT,PRENAME)
+
+mkdir(OUTPUT);
+
+MAXY=max([max(STD15) max(STD25)]);
+plot(TIME,STD15,'-o',TIME,STD25,'-s'), grid
+ylim([0 MAXY*1.1])
+xlabel('Time (min)')
+ylabel('STD')
+legend('15 fps','25 fps');
+print(gcf,fullfile(OUTPUT,filesep,[PRENAME 'STD.eps']),'-deps')
+
+MAXY=max([max(MEAN15) max(MEAN25)]);
+plot(TIME,MEAN15,'-o',TIME,MEAN25,'-s'), grid
+ylim([0 MAXY*1.1])
+xlabel('Time (min)')
+ylabel('MEAN')
+legend('15 fps','25 fps');
+print(gcf,fullfile(OUTPUT,filesep,[PRENAME 'MEAN.eps']),'-deps')
+
+MAXY=max([max(AVD15) max(AVD25)]);
+plot(TIME,AVD15,'-o',TIME,AVD25,'-s'), grid
+ylim([0 MAXY*1.1])
+xlabel('Time (min)')
+ylabel('AVD')
+legend('15 fps','25 fps');
+print(gcf,fullfile(OUTPUT,filesep,[PRENAME 'AVD.eps']),'-deps')
+end

### 2019-02-24 mcode/mcode-freq:15:15:60/func_dir_std.m

@@ -1,0 +1,40 @@
+function [STD MEAN AVD STDF TIME h]=func_dir_std(DIRROOT,varargin)
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    h=get_fir_filter(40,0.5,'high');
+    %[AH FREQN]=freqmod(h,40);
+    %plot(FREQN,AH,'-o');
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+    %H=DIRROOT
+    STDF=zeros(1,11);
+    STD=zeros(1,11);
+    MEAN=zeros(1,11);
+    AVD=zeros(1,11);
+    TIME=[0:10];
+    for II=0:10
+        DIR=fullfile(DIRROOT,[num2str(II) 'min'],'ROI');
+
+        %% To filenames: 'img1coffee.bmp', 'img2coffee,bmp', ..., 'img100coffee.bmp'
+        DATA = datapack(DIR,'%d',1,512,'bmp');
+
+        [DATAF DATA1] = firfilterbank(DATA,h,'MODE0');        
+
+        if(nargin>1)
+            NN=round(size(DATA,3)/varargin{1});
+            ID=1+(0:(NN-1))*varargin{1};
+            DATA=DATA(:,:,ID);
+
+            DATAF=DATAF(:,:,ID);
+        endif 
+        [C D E]=stdcont(DATA,'off');
+        [CF DF EF]=stdcont(DATAF,'off');
+        GAVD=graphavd(DATA,'off');
+
+        STD(II+1)=mean(mean(D));
+        STDF(II+1)=mean(mean(DF));
+        MEAN(II+1)=mean(mean(E));
+        AVD(II+1)=mean(mean(GAVD));
+    end
+    
+end

### 2019-02-24 mcode/mcode-freq:15:15:60/func_programa_plot2.m

@@ -1,0 +1,59 @@
+function func_programa_plot2(   STD15,MEAN15,AVD15,STDF15,...
+                                STD30,MEAN30,AVD30,STDF30,...
+                                STD45,MEAN45,AVD45,STDF45,...
+                                STD60,MEAN60,AVD60,STDF60,...
+                                H,TIME,OUTPUT,PRENAME,YLABELPLUS)
+
+FONTSIZE=17;
+mkdir(OUTPUT);
+
+set(0, "defaultlinemarkersize", 15);
+
+[AH FREQN]=freqmod(H,100);
+plot(FREQN,AH,'-o');
+xlabel('Normalizaed frequency')
+ylabel('Filter')
+set(gca(), 'fontsize', FONTSIZE);
+print(gcf,fullfile(OUTPUT,filesep,[PRENAME 'STDF-H.eps']),'-deps',['-F:',int2str(FONTSIZE)])
+
+
+MAXY=max([max(STD15) max(STD30) max(STD45) max(STD60)]);
+plot(TIME,STD15,'-o',TIME,STD30,'-s',TIME,STD45,'-<',TIME,STD60,'-*'), grid
+ylim([0 MAXY*1.1])
+xlabel('Time (min)')
+ylabel([YLABELPLUS 'STD'])
+hl=legend('15 fps','30 fps','45 fps','60 fps');
+set(hl,'location','southeast');
+set(gca(), 'fontsize', FONTSIZE);
+print(gcf,fullfile(OUTPUT,filesep,[PRENAME 'STD.eps']),'-deps',['-F:',int2str(FONTSIZE)])
+
+MAXY=max([max(MEAN15) max(MEAN30) max(MEAN45) max(MEAN60)]);
+plot(TIME,MEAN15,'-o',TIME,MEAN30,'-s',TIME,MEAN45,'-<',TIME,MEAN60,'-*'), grid
+ylim([0 MAXY*1.1])
+xlabel('Time (min)')
+ylabel('MEAN')
+legend('15 fps','30 fps','45 fps','60 fps');
+set(gca(), 'fontsize', FONTSIZE);
+print(gcf,fullfile(OUTPUT,filesep,[PRENAME 'MEAN.eps']),'-deps',['-F:',int2str(FONTSIZE)])
+
+MAXY=max([max(AVD15) max(AVD30) max(AVD45) max(AVD60)]);
[…]

### 2019-02-24 mcode/mcode-freq:15:15:60/programa.m

@@ -1,0 +1,35 @@
+%
+
+pkg load bsltl
+
+OUTPUT='/home/fernando/Downloads/ROLANDO/FPS_f11';
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+DIRSRC=fullfile(OUTPUT,filesep,'15fps');
+[STD15 MEAN15 AVD15 STDF15 TIME H]=func_dir_std(DIRSRC);
+
+DIRSRC=fullfile(OUTPUT,filesep,'30fps');
+[STD30 MEAN30 AVD30 STDF30 TIME H]=func_dir_std(DIRSRC);
+
+DIRSRC=fullfile(OUTPUT,filesep,'45fps');
+[STD45 MEAN45 AVD45 STDF45 TIME H]=func_dir_std(DIRSRC);
+
+DIRSRC=fullfile(OUTPUT,filesep,'60fps');
+[STD60 MEAN60 AVD60 STDF60 TIME H]=func_dir_std(DIRSRC);
+
+func_programa_plot2(   STD15,MEAN15,AVD15,STDF15,...
+                       STD30,MEAN30,AVD30,STDF30,...
+                       STD45,MEAN45,AVD45,STDF45,...
+                       STD60,MEAN60,AVD60,STDF60,...
+                       H,TIME,'dir_FPS_f11_raw','FPS_f11_raw','');
+
+func_programa_plot2(   STD15/max(STD15),MEAN15,AVD15/max(AVD15),STDF15/max(STDF15),...
+                       STD30/max(STD30),MEAN30,AVD30/max(AVD30),STDF30/max(STDF30),...
+                       STD45/max(STD45),MEAN45,AVD45/max(AVD45),STDF45/max(STDF45),...
+                       STD60/max(STD60),MEAN60,AVD60/max(AVD60),STDF60/max(STDF60),...
+                       H,TIME,'dir_FPS_f11_norm1','FPS_f11_norm1','Normalized ');
+
+

### 2019-02-24 mcode/mcode-maiz-freq:15:15:60/func_dir_std_1time.m

@@ -1,0 +1,50 @@
+function [STD MEAN AVD STDF h]=func_dir_std_1time(DIRROOT,varargin)
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    h=get_fir_filter(40,0.5,'high');
+    %[AH FREQN]=freqmod(h,40);
+    %plot(FREQN,AH,'-o');
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+    %H=DIRROOT
+    STDF=0;    STD=0;
+    MEAN=0;    AVD=0;
+
+        DIR=fullfile(DIRROOT,'ROI');
+        %% To filenames: 'img1coffee.bmp', 'img2coffee,bmp', ..., 'img100coffee.bmp'
+        DATA = datapack(DIR,'%d',1,512,'bmp');
+        
+        [DATAF DATA1] = firfilterbank(DATA,h,'MODE0');
+        
+        %% if(nargin>1)
+        %%     NN=round(size(DATA,3)/varargin{1});
+        %%     ID=1+(0:(NN-1))*varargin{1};
+        %%     DATA=DATA(:,:,ID);
+        %%     
+        %%     DATAF=DATAF(:,:,ID);
+        %% endif 
+        
+        
+        [C D E]=stdcont(DATA,'off');        
+        [CF DF EF]=stdcont(DATAF,'off');
+        GAVD=graphavd(DATA,'off');
+        
+        STD=mean(mean(D));
+        STDF=mean(mean(DF));
+        MEAN=mean(mean(E));
+        AVD=mean(mean(GAVD));
+
+
+        %% [C D E]=stdcont(DATA,'off'); 
+        %% imagesc(D);  
+        %% colormap(jet);
+        %% M=200;Sigma=2;
+        %% [Y POINTS]= thsp_gaussian(DATA,M,Sigma,gcf,'on');
+        %% [YF ]= thsp_points(DATAF, POINTS); 
+        
+        %% AVD= avd(coom(Y));
+        %% STD= mean(std(Y'));
+        %% MEAN= mean(mean(Y'));
+
+        %% STDF= mean(std(YF'));
+end

### 2019-02-24 mcode/mcode-maiz-freq:15:15:60/func_programa_plot3.m

@@ -1,0 +1,48 @@
+function func_programa_plot3(   STD15,MEAN15,AVD15,STDF15,...
+                                STD30,MEAN30,AVD30,STDF30,...
+                                STD45,MEAN45,AVD45,STDF45,...
+                                STD60,MEAN60,AVD60,STDF60,...
+                                H,OUTPUT,PRENAME)
+
+FONTSIZE=17;
+mkdir(OUTPUT);
+
+[AH FREQN]=freqmod(H,100);
+plot(FREQN,AH,'-o');
+xlabel('Normalizaed frequency')
+ylabel('Filter')
+set(gca(), 'fontsize', FONTSIZE);
+print(gcf,fullfile(OUTPUT,filesep,[PRENAME 'STDF-H.eps']),'-deps',['-F:',int2str(FONTSIZE)])
+
+
+MEANVAL=[MEAN15 MEAN30 MEAN45 MEAN60];
+FREQ=[15 30 45 60];
+plot(FREQ,MEANVAL,'-s'), grid
+xlabel('Fs (Hertz)')
+ylabel('MEAN')
+ylim([0 1.1*max(MEANVAL)])
+legend(['MEAN : ' num2str(MEAN60*100/MEAN15) '%']);
+set(gca(), 'fontsize', FONTSIZE);
+print(gcf,fullfile(OUTPUT,filesep,[PRENAME 'ALLMEAN.eps']),'-deps',['-F:',int2str(FONTSIZE)])
+
+
+AVDVAL=[AVD15 AVD30 AVD45 AVD60];
+STDVAL=[STD15 STD30 STD45 STD60];
+STDFVAL=[STDF15 STDF30 STDF45 STDF60];
+FREQ=[15 30 45 60];
+plot(FREQ,STDVAL,'-s',FREQ,AVDVAL,'-o',FREQ,STDFVAL,'-*'), grid
+xlabel('Fs (Hertz)')
+ylabel('Index value')
+legend(['STD  : ' num2str(STD60*100/STD15) '%'],['AVD  : ' num2str(AVD60*100/AVD15) '%'],['STDF : ' num2str(STDF60*100/STDF15) '%']);
+set(gca(), 'fontsize', FONTSIZE);
+print(gcf,fullfile(OUTPUT,filesep,[PRENAME 'ALL.eps']),'-deps',['-F:',int2str(FONTSIZE)])
+
+%% 
[…]

### 2019-02-24 mcode/mcode-maiz-freq:15:15:60/programa.m

@@ -1,0 +1,28 @@
+%
+
+pkg load bsltl
+
+OUTPUT='/home/fernando/Downloads/ROLANDO/Semilla 3_3dias/3dias';
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+DIRSRC=fullfile(OUTPUT,filesep,'15fps');
+[STD15 MEAN15 AVD15 STDF15 H]=func_dir_std_1time(DIRSRC);
+
+DIRSRC=fullfile(OUTPUT,filesep,'30fps');
+[STD30 MEAN30 AVD30 STDF30 H]=func_dir_std_1time(DIRSRC);
+
+DIRSRC=fullfile(OUTPUT,filesep,'45fps');
+[STD45 MEAN45 AVD45 STDF45 H]=func_dir_std_1time(DIRSRC);
+
+DIRSRC=fullfile(OUTPUT,filesep,'60fps');
+[STD60 MEAN60 AVD60 STDF60 H]=func_dir_std_1time(DIRSRC);
+
+func_programa_plot3(   STD15,MEAN15,AVD15,STDF15,...
+                       STD30,MEAN30,AVD30,STDF30,...
+                       STD45,MEAN45,AVD45,STDF45,...
+                       STD60,MEAN60,AVD60,STDF60,...
+                       H,'dir_Semilla_3_3dias','FPS_Semilla_3_3dias');
+

### 2019-03-25 article/article_1.tex
mejorando el texto

@@
 in a dynamic speckle analysis, affect the value of some dynamic speckle index, 
-in this case: the absolute value of the differences ($AVD$) index, the temporal 
+in this case: the absolute value of the differences index, the temporal 
 speckle standard deviation index and the temporal 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
-Dynamic laser speckle is a phenomenon that is 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%1) Anuncie o tema e o problema do artigo (forma de pergunta + definiçoes)
+
+The dynamic speckle analysis over biological samples has become  currently  an important
+study topic\cite{catalano2019viability,rivera2019sound,gonzalez2018diode,Silva2018,braga2017dynamic} 
+to determine the level of biological activity. 
+The importance of technical aspects of dynamic speckle analysis,
+as the stability of laser illumination level, was analized \cite{gonzalez2018diode}; 
+and was showed as indexes as
+the absolute values of the differences \cite{cardoso2014,rivera2017selection} are affected in your values
+by the variation of illumination level. Thus, It is necessary analyze the effect
+of technical parameters that affect the perceived illumination level; In these sense
+analyze the effect of sampling frequency in a dynamic speckle analysis
+
+%2) Exponha qual será o percurso (defina seçoes)
+%3) Resgate a problematica( Importancia do problema de pesquisa - extenda primer passo)
+%4) Relevancia do artigo(importancia para outros del artigo publicado)
+%5) Anuncie a hipotesi
+%6) Anuncie os objetivos (receita pra demostrar a h.)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{System description}
@@
 the $Exposure$ represent the photography integration time and $E$ the effective time
-between photographs.
+between photographs; 
+the difference between these two exposures arise from $Offset$ time, 
+that is the time between end and start of a photography.
 \begin{table}[h!]
@@
  has 512 images of 147 pixels of height and 166 pixels of width.
- They were use 4 different sampling frequency to the images in each package,
+ They were use 4 different sampling frequencies to the images in each package,
  being these frequencies $15$, $30$, $45$ and $60$ hz.
@@
  being these frequencies $15$, $30$, $45$ and $60$ hz.
- Each package has 512 images of 29 pixels of height and 31 pixels of width.
+ Each package has 512 images of $15$ pixels of height and $15$ pixels of width.
 
@@
 \end{figure}
-where, $P(t)$ is an image data package at the time $t$ minutes.
-The $MEAN$ block represent the calculus of a temporal speckle mean index from 
+where, $P(t)$ is an image data package at the time $t$ minutes, 
+being that this package has $N$ images and $M$ pixels, where $P_{n,m}(t)$ 
+define the $n$-th image and $m$-th pixel, for all $1 \leq n \leq N$, $1 \leq m \leq M$.
+The $MEAN$ block represents the calculus of a temporal speckle mean index from 
 the package $P(t)$, returning the value $MEAN(t)$, as exposed in the Section \ref{sec:mean}. 
-The $AVD$ block represent the calculus of a absolute values of the differences index from 
+The $AVD$ block represents the calculus of an absolute values of the differences index from 
 the package $P(t)$, returning the value $AVD(t)$, as exposed in the Section \ref{sec:avd}. 
-The $STD$ block represent the calculus of a temporal speckle standard deviation index from 
+The $STD$ block represents the calculus of a temporal speckle standard deviation index from 
 the package $P(t)$, returning the value $STD(t)$, as exposed in the Section \ref{sec:std}.
@@
 the block $HPF$ represents a digital finite impulse response ``high-pass filter'' 
-with order $40$ and cut-off at $0.25F_s$ that causes to have the at end of path
-the $STDF(t)$ index value, a frequency filtered version of $STD(t)$.
+with order $40$ and cut-off at $0.25F_s$ and this block filter the $P(t)$ package and return $Q(t)$,
+that causes to have at end of path the $STDF(t)$ index value.
 According the information of the data packages, 
-we will have indexes values, for each minutes during 10 minutes.
+we will have speckle indexes values, for each minute during 10 minutes.
 
@@
 The activity analysis of a corn seed, 
-uses the information of data package seen in the Section \ref{subsec:data1}.
+uses the information of data package seen in the Section \ref{subsec:data2}.
 We analyze this information of similar way to the seen in the Section \ref{subsec:test1},
-with the difference that is taken an data package at the time $t$ (3 days of germination).
+with the difference that is taken an data package at the time $t$ (3 days of germination)
+and a sampling frequency $F_s$.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Test 3: Frequency band activity analysis}
+\label{subsec:test3}
+
+The Fig. \ref{fig:test3} represents the frequency band analysis method of data package $P$, 
+acquired  with a sampling frequency of $F_s$. This package pass through the $BPF$ block
+described in the Sec \ref{sec:stdb}, with a frequency band pass between $f_1(l)$ and $f_2(l)$,
+according the Eq. \ref{eq:f1f2}, where $l$ represent the band so that $1\leq l\leq L$,
+being $L$ the quantity of analysis frequency bands; 
+thus, we obtaining the  $R$ package (a filtered version of $P$). Later, It is processed 
+a $\sigma$ block, where It is calculate the $\sigma_{m}$ value to each pixel in the package $R$,
+as described in the Sec \ref{sec:std}. Finally, 
+an image is obtained and It is designed with the variable $STDB$.
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.55\columnwidth]{test3.eps}
+\caption{Frequency band analysis of a data package.}
+\label{fig:test3}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Theoretical definitions}
@@
 
-\subsection{temporal speckle mean index}
+In the next subsections we use the variable $P$ to define $P(t)$ in any time $t$.
+
+\subsection{$MEAN$ index }
 \label{sec:mean}
 
-\subsection{Absolute Values of the Differences (AVD)}
+The temporal speckle mean index ($\mu_{m}$) \cite{Nothdurft:05} calculates the mean
+value of the illumination level to the $m$-th pixel in the package $P$, It is implemented
+with the Eq. \ref{eq:mu},
+\begin{equation}\label{eq:mu}
+\mu_{m} = \sum \limits_{n=1}^{N} \frac{P_{n,m}}{N}.
+\end{equation}
+Finally, the $MEAN$ index is the mean value of all $\mu_{m}$ results,
+as can be viewed in the Eq. \ref{eq:MEAN},
+\begin{equation}\label{eq:MEAN}
+MEAN = \sum \limits_{m=1}^{M} \frac{\mu_{m}}{M}.
+\end{equation}
+
+\subsection{$AVD$ index}
 \label{sec:avd}
-%% Following the working flow in Fig. 2, the randomly-selected points in the ROI were 
-%% analysed, with respect to their behaviour in time, by means of the Absolute Values 
-%% of the Differences (AVD) method [35] using the data in the COM without 
-%% normalization. The AVD method can be expressed by Equation (1):
 
-%% where the COM is the Co-Occurrence Matrix related to the THSP, and the i and j 
-%% variables represent the line i and the column j of each point of the COM matrix.
+The Absolute Values of the Differences ($AVD_{m}$) \cite{cardoso2014,rivera2017selection} calculates the mean
+value of the absolute differences in the illumination level of the $m$-th pixel in the package $P$, It is implemented
+with the Eq. \ref{eq:avd0},
+\begin{equation}\label{eq:avd0}
+AVD_{m} = \sum \limits_{n=2}^{N} \frac{|P_{n,m}-P_{n-1,m}|}{N}.
+\end{equation}
+Finally, the $AVD$ index is the mean value of all $AVD_{m}$ results,
+as can be viewed in the Eq. \ref{eq:AVD},
+\begin{equation}\label{eq:AVD}
+AVD = \sum \limits_{m=1}^{M} \frac{AVD_{m}}{M}
+\end{equation}
 
-Frequency composition from $F_s/4$ until $F_s/2$ Hz like as  $HPF$ of first order.
+%Frequency composition from $F_s/4$ until $F_s/2$ Hz like as  $HPF$ of first order.
 
-\subsection{Temporal speckle standard deviation index}
+\subsection{$STD$ index}
 \label{sec:std}
-Frequency composition from $0$ until $F_s/2$ Hz like as  $HPF$ of first order.
 
-\subsection{Filtered temporal speckle standard deviation index}
+The temporal speckle standard deviation index ($\sigma_{m}$) \cite{Nothdurft:05} calculates the standard deviation
+value of the illumination level to the $m$-th pixel in the package $P$, It is implemented
+with the Eq. \ref{eq:sigma},
+\begin{equation}\label{eq:sigma}
+\sigma_{m}^2 = \sum \limits_{n=1}^{N} \frac{(P_{n,m}-\mu_{m})^2}{N}.
+\end{equation}
+Finally, the $STD$ index is the mean value of all $\sigma_{m}$ results,
+as can be viewed in the Eq. \ref{eq:STD},
+\begin{equation}\label{eq:STD}
+STD = \sum \limits_{m=1}^{M} \frac{\sigma_{m}}{M}
+\end{equation}
+
+%Frequency composition from $0$ until $F_s/2$ Hz like as  $HPF$ of first order.
+
+\subsection{$HPF$ block}
 \label{sec:stdf}
-Frequency composition from $0$ until $F_s/2$ Hz like as  $HPF$ of first order.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The high-pass filter ($HPF$) block It is implemented with a finite impulse 
+response ($FIR$)\cite{saramaki1993finite} filter
+of order 40 and cut-off at $0.25F_s$. 
+The 41 values in the filter are represented with $h(i)$, for all $0 \leq i\leq 40$ and zero in others cases, so that
+if we send a data package $P$ through the $HPF$ block we obtain a data package $Q$,
+as can be seen in the Eq. \ref{eq:fir},
+\begin{equation}\label{eq:fir}
+Q_{n,m} = \sum_{k=1}^{N} P_{k,m} h(n-k+20}).
+\end{equation}
 
+%Frequency composition from $0$ until $F_s/2$ Hz like as  $HPF$ of first order.
+
+\subsection{$BPF$ block}
+\label{sec:stdb}
+
+The band-pass filter ($BPF$) block, 
+It is implemented similarly as the see in Sec. \ref{sec:stdf}, 
+ with  a $FIR$ filter of order 40 but with a cut-off in $f_1(l)$ and $f_2(l)$, 
+\begin{equation}\label{eq:f1f2}
+\left [ f_1(l),~f_2(l)\right ] = \left [\frac{(l-1)}{L},~\frac{l}{L} \right ]\frac{F_s}{2},
+\end{equation}
+representing $l$, for all $1 \leq l \leq L$, the $l$-th band of $L$ parts; so that each band has $\frac{F_s}{2L}$ Hz.
+The filter is represented with $g(i)$, for all $0 \leq i\leq 40$ and zero in others cases, so that
+if we send a data package $P$ through the $BPF$ block we obtain a data package $R$,
+as can be seen in the Eq. \ref{eq:firb},
+\begin{equation}\label{eq:firb}
+R_{n,m} = \sum_{k=1}^{N} P_{k,m}~g(n-k+20}).
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Numerical results} 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Result of test 1}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Result of test 2}
@@
 
+This test shows the analyze result of a corn seed  with 3 days of germination,
+with the sampling frequencies: $15$, $30$, $45$ and $60$Hz.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The Figure \ref{fig:MEANtest2} shows the $MEAN(t)$ index,
+in the test described in the Section \ref{subsec:test2};
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{FPS_Semilla_3_3diasALLMEAN.eps}
+    \caption{$MEAN$ index value in the germinated corn seed.}\label{fig:MEANtest2}
+\end{figure}
+The figure shows as the index decrease your value, 
+with the increment of sampling frequency in the datapack,
+so that between $15$ Hz until $60$ Hz, the index value reaches the $20.137\%$ of your value.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The Figure \ref{fig:INDEXtest2} shows the $AVD(t)$, $STD(t)$ and $STDF(t)$ indexes,
+in the test described in the Section \ref{subsec:test2};
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{FPS_Semilla_3_3diasALL.eps}
+    \caption{$AVD(t)$, $STD(t)$ and $STDF(t)$ indexes values in the germinated corn seed.}\label{fig:INDEXtest2}
+\end{figure}
+The similar way that in the Figure \ref{fig:MEANtest2},
+the index decrease your value with the grow of $F_s$,
+so that the indexes, 
+$AVD(t)$, $STD(t)$ and $STDF(t)$, 
+reaches the $22.2426\%$, $19.2578\%$ and $20.3541\%$ of your values, 
+respectively.
+
+\subsection{Result of test 3}
+\label{subsec:resulttest3}
+The Table \ref{table:2} shows the result of calculating the $STDB$ image
+in different frequency bands over a package $P$, see Sec. \ref{subsec:test3}, 
+The package represents  a corn seed as in the Section \ref{subsec:data2};
+where, we have packages sampled with the frequencies: $15$, $30$, $45$ and $60$ Hz, as
+can be seen in the first column of table.
+
+%~\\
+\begin{table}[h!]
+\includegraphics[width=\textwidth]{colorbar.eps}
+\includegraphics[width=\textwidth]{freq1.eps}
+\caption{frequency band analysis}
+\label{table:2}
+\end{table}
+In the other columns we can see the results of until $8$ frequency bands of package $P$,
+these bands are represented in the first line of table, were $l$ indicates the position of frequency band
+in crescent order relative to the frequency components. Thus, we have 
+these frequency bands limited on: $0$, $3.75$, $7.5$, $11.25$, $15$, $18.75$, $22.5$, $26.25$ and $30$Hz.
+So that, the package sampled in $15$hz was divided in $L=2$ frequency bands, 
+in $30$hz was divided in $L=4$ frequency bands, 
+in $45$hz was divided in $L=6$ frequency bands and finally
+in $60$hz was divided in $L=8$ frequency bands.
+
+The matrices $STDB$ are represented using a color palette, 
+that goes from dark blue to dark red color, representing of ascendant way the values
+in each pixel in all matrices. It is evident how the index values decreases with
+the increment of frequency sampling $F_s$ in each one of 8 frequency bands, 
+the index values also decrease with the increment of the position of frequency band,
+being the best analysis case, 
+in the sense of differentiating better places of lower and higher index, 
+to a frequency sampling of $15$ hz and a frequency band between $0$ Hz and $3.75$ Hz.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Analysis results} 
@@
 
-\subsection{Analysis of results: test 1}
-\label{subsec:analysistest1}
-In the results of ink drying process test, seen in Section \ref{subsec:resulttest1},
-we can observe in the Figure \ref{fig:MEANtest1}, that the index shows a relation 
-between the value of curve and the sampling frequency of datapack. 
+In the results seen in Section \ref{sec:numericalresults},
+we can observe in the Figure \ref{fig:MEANtest1} and \ref{fig:MEANtest2}, 
+that the indexes show a relation between the value of curve and the sampling frequency of datapack. 
 How is known \cite{Nothdurft:05}, the temporal speckle mean index is related to 
-the observed illumination level in the surface of study material.
-Thus, we can conclude that the level of illumination perceived by the camera decrease
-with the increment of sampling frequency. 
-This is because that the exposition time is modified, see Section \ref{subsec:expositiontime}, 
-with the alteration of sampling frequency, 
+the observed illumination level in the surface of study material and correspond to zero frequency of the signal (datapack).
+Thus, we can conclude that the level of illumination, perceived by the camera, 
+decrease with the increment of sampling frequency. 
+This is because that the exposition time is modified with the alteration of sampling frequency, 
+see Section \ref{subsec:expositiontime}, 
 so that less lighting is used to take the picture and consequently the 
 temporal speckle mean index decrease in  your value.
-The modification of exposition time also affect other indexes, 
-how can it be seen in the Figures \ref{fig:AVDtest1}, \ref{fig:STDtest1} and  \ref{fig:STDFtest1}, 
-where these indexes decrease your values in concordance with the decrease of exposition time.
+In this sense, It is important have careful in to choose a sampling frequency
+that give us an index value superior to noise level of test or the quantization level of the camera.
+
+The modification of exposition time also affect  and limit other indexes,
+remember that we have a quantization level between $0$ and $255$ in the camera. 
+We can see this interference in the Figures \ref{fig:AVDtest1}, \ref{fig:STDtest1}, \ref{fig:STDFtest1} and \ref{fig:INDEXtest2}, 
+where the $AVD(t)$, $STD(t)$ and $STDF(t)$ indexes decrease your values in concordance with the decrease of exposition time.
 Other way in that  the sampling frequency affect the values of indexes,
-It is that it limits the band of signal frequency analyzed; for example,
-a sampling frequency $F_s$ causes that the analyzed signal frequency band will be between $0 Hz$ and $F_s/2~Hz$.
-Thus, in this context we have an index as $MEAN(t)$ that use information at  $0~Hz$ only, 
-the index $STD(t)$ that use information between $\langle \left. 0, F_s/2 \right ] Hz$, 
+It is that, it limits the frequency band of analyzed signal; for example,
+a sampling frequency $F_s$, by the Nyquist theorem \cite{Nyquist,Shannon}, 
+causes that the frequency band of analyzed signal (datapack)  will be between $0 Hz$ and $F_s/2~Hz$.
+Thus, in this context we have an index as $STD(t)$ that uses information between $\langle \left. 0, F_s/2 \right ] Hz$, 
 and be other side we have indexes as the $AVD(t)$ and the $STDF(t)$ index, that use information of half frequency band, 
@@
 In the comparison between $STD(t)$ vs  $\{$ $STDF(t)$ and $AVD(t)$ $\}$, 
-we can observe how the half part  use of frequency band causes the decrease of curves values, 
-but considerably good values in the maximum excursion of the curve. By other side,
+we can see how the use of half, of entire frequency band, causes the decrease in the values of the curves, 
+but give us considerably good values in the maximum excursion of the curve. By other side,
 in the case of ink drying process, the use of complete frequency band, 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+It is necessary to highlight the importance of to choose the least value of sampling frequency $F_s$;
+so that, 
+the frequency band of signal contain the frequency components with the information that you want to analyze;
+so that, the values of indexes have the greatest values and consequently a good excursion, 
+when compared with an inert part of sample; 
+By example, in the Table. \ref{table:2} is analyzed a corn seed, 
+we can see as the major values of indexes are obtained to a $F_s=15$ Hz, 
+analyzing frequency component between $0$ hz and $7.5$ Hz. At this point,
+an additionally result is evident, when we ask ourselves, 
+What is the best frequency band? where according with the test, we see that for
+all frequency bands, 
+the best frequency band, to the case of corn seed, is the one with the components with less frequency.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Acknowledgment}
@@
 
-%----------------------------------------------------------------------------------------
-%	REFERENCE LIST
-%----------------------------------------------------------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Bibliography}
@@
 
-%----------------------------------------------------------------------------------------
-
 \end{document}

### 2019-03-25 article/images/freq1/Make-freq1.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+
+latex freq1.tex
+dvips -E -o freq1.eps freq1.dvi
+
+rm -f freq1.aux  
+rm -f freq1.log  
+rm -f freq1.dvi  
+

### 2019-03-25 article/images/freq1norm/Make-freq1.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+
+latex freq1norm.tex
+dvips -E -o freq1norm.eps freq1norm.dvi
+
+rm -f freq1norm.aux  
+rm -f freq1norm.log  
+rm -f freq1norm.dvi  
+

### 2019-03-25 mcode/mcode-maiz-freq:15:15:60/func_dir_std_1time.m

@@ -1,5 +1,5 @@
 function [STD MEAN AVD STDF h]=func_dir_std_1time(DIRROOT,varargin)
-
+    REGION='REGION'
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     h=get_fir_filter(40,0.5,'high');
     %[AH FREQN]=freqmod(h,40);
@@ -10,7 +10,7 @@ function [STD MEAN AVD STDF h]=func_dir_std_1time(DIRROOT,varargin)
     STDF=0;    STD=0;
     MEAN=0;    AVD=0;
 
-        DIR=fullfile(DIRROOT,'ROI');
+        DIR=fullfile(DIRROOT,REGION);
         %% To filenames: 'img1coffee.bmp', 'img2coffee,bmp', ..., 'img100coffee.bmp'
         DATA = datapack(DIR,'%d',1,512,'bmp');
         

### 2019-03-25 mcode/mcode-maiz-freqfreq/func_dir_std_1freq.m

@@ -1,0 +1,75 @@
+function [STD MEAN AVD STDF h]=func_dir_std_1freq(DIRROOT,NUM,OUTPUT,DMAX,FACTOR)
+    REGION='REGION';
+    N=2*FACTOR;
+    H=cell(1,N);
+    Fs=cell(1,N);
+
+    mkdir(fullfile(OUTPUT,[num2str(NUM) 'fps']));
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    for II=1:N    
+        H{II}=get_fir_filter(40,(II-1)/N+[0.0 1.0]/N,'bandpass');   
+        F{II}=((II-1)/N+[0.0 1.0]/N)*NUM/2;
+        % [AH FREQN]=freqmod(H{II},400);
+        % plot(FREQN,AH,'-o');
+    endfor
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+    %DIR=fullfile(DIRROOT,[num2str(NUM) 'fps'],REGION);
+    DIR=fullfile(DIRROOT,[num2str(NUM) 'fps'],REGION);
+    %% To filenames: 'img1coffee.bmp', 'img2coffee,bmp', ..., 'img100coffee.bmp'
+    DATA = datapack(DIR,'%d',1,512,'bmp');
+    %DATA=DATA(180:(end-100),150:(end-150),:);
+
+    %% pkg load image
+    %% FF = fspecial("average", 3);    
+
+    [C D E]=stdcont(DATA,'off');
+    %% D = imfilter(D, FF);
+    %% E = imfilter(E, FF);
+
+    %DMAX=max(max(D));
+    imagesc(E); title('MEAN')  
+    colormap(jet);
+    colorbar;
+    FileName=fullfile(OUTPUT,[num2str(NUM) 'fps'],'MEAN.eps');
+    print(gcf,FileName,'-depsc')
+
+    imagesc(D); title('STD')  
+    colormap(jet);
+    colorbar;
+    FileName=fullfile(OUTPUT,[num2str(NUM) 'fps'],'STD.eps');
+    print(gcf,FileName,'-depsc')
+
[…]

### 2019-03-25 mcode/mcode-maiz-freqfreq/func_dir_std_2freq.m

@@ -1,0 +1,78 @@
+function [STD MEAN AVD STDF h]=func_dir_std_2freq(DIRROOT,NUM,OUTPUT,FACTOR)
+    REGION='REGION';
+    N=2*FACTOR;
+    H=cell(1,N);
+    Fs=cell(1,N);
+
+    mkdir(fullfile(OUTPUT,[num2str(NUM) 'fps']));
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    for II=1:N    
+        H{II}=get_fir_filter(40,(II-1)/N+[0.0 1.0]/N,'bandpass');   
+        F{II}=((II-1)/N+[0.0 1.0]/N)*NUM/2;
+        % [AH FREQN]=freqmod(H{II},400);
+        % plot(FREQN,AH,'-o');
+    endfor
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+    %DIR=fullfile(DIRROOT,[num2str(NUM) 'fps'],REGION);
+    DIR=fullfile(DIRROOT,[num2str(NUM) 'fps'],REGION);
+    %% To filenames: 'img1coffee.bmp', 'img2coffee,bmp', ..., 'img100coffee.bmp'
+    DATA = datapack(DIR,'%d',1,512,'bmp');
+    %DATA=DATA(180:(end-100),150:(end-150),:);
+    
+    %% pkg load image
+    %% FF = fspecial("average", 3);
+
+    [C D E]=stdcont(DATA,'off');
+    %% D = imfilter(D, FF);
+    %% E = imfilter(E, FF);
+
+    imagesc(E); title('MEAN')  
+    colormap(jet);
+    colorbar;
+    FileName=fullfile(OUTPUT,[num2str(NUM) 'fps'],'MEAN.eps');
+    print(gcf,FileName,'-depsc')
+
+    imagesc(D); title('STD')  
+    colormap(jet);
+    colorbar;
+    FileName=fullfile(OUTPUT,[num2str(NUM) 'fps'],'STD.eps');
+    print(gcf,FileName,'-depsc')
+
+    DMAX=0;
[…]

### 2019-03-25 mcode/mcode-maiz-freqfreq/programa.m

@@ -1,0 +1,43 @@
+%
+
+pkg load bsltl
+
+INPUT='/home/fernando/Downloads/ROLANDO/Semilla 3_3dias/3dias';
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+OUTPUT='output'
+mkdir(OUTPUT);
+DMAX=44;
+
+func_dir_std_1freq(INPUT,15,OUTPUT,DMAX,1);
+func_dir_std_1freq(INPUT,30,OUTPUT,DMAX,2);
+func_dir_std_1freq(INPUT,45,OUTPUT,DMAX,3);
+func_dir_std_1freq(INPUT,60,OUTPUT,DMAX,4);
+
+close all
+ax = axes;
+colormap ("jet");
+h=colorbar(ax,"northoutside");
+caxis([0 DMAX]);
+set(ax,'visible','off');
+print(fullfile(OUTPUT,'colorbar.eps'),'-depsc','-tight');
+
+
+
+
+OUTPUT='output-norm'
+mkdir(OUTPUT);
+
+func_dir_std_2freq(INPUT,15,OUTPUT,1);
+func_dir_std_2freq(INPUT,30,OUTPUT,2);
+func_dir_std_2freq(INPUT,45,OUTPUT,3);
+func_dir_std_2freq(INPUT,60,OUTPUT,4);
+
+
+
+
+
+

### 2019-03-26 article/article_1.tex
trucomanx-formulation

@@
 
-The dynamic speckle analysis over biological samples has become  currently  an important
+The dynamic laser speckle analysis has become in the last years  an important
 study topic\cite{catalano2019viability,rivera2019sound,gonzalez2018diode,Silva2018,braga2017dynamic} 
-to determine the level of biological activity. 
-The importance of technical aspects of dynamic speckle analysis,
-as the stability of laser illumination level, was analized \cite{gonzalez2018diode}; 
-and was showed as indexes as
-the absolute values of the differences \cite{cardoso2014,rivera2017selection} are affected in your values
+to determine the  activity level of biological materials. 
+The importance of technical aspects of dynamic laser speckle analysis,
+as the stability of laser illumination level has been  analyzed \cite{gonzalez2018diode}; 
+and also It was studed as indexes,
+as absolute values of the differences \cite{cardoso2014,rivera2017selection} are affected in your values
 by the variation of illumination level. Thus, It is necessary analyze the effect
 of technical parameters that affect the perceived illumination level; In these sense
-analyze the effect of sampling frequency in a dynamic speckle analysis
+we analyze the effect of sampling frequency in a dynamic laser speckle analysis.
 
@@
 
-In this work were presented comparisons of behavior of three dynamic speckle indexes
+In this work were presented comparisons of behavior of three dynamic laser speckle indexes
 subject to different values of sampling frequency, thus we concluded that:

### 2019-04-04 article/article_1.tex
acabe de escribir primera version, pero falta agregar un grafico.

--- 2019-03-25 article/article_1.tex
@@
 speckle mean index.
-we show that  the dynamic speckle index value decrease your maximum excursion with 
-the grow of sampling frequency because this affect directly the time integration 
+we show that  the dynamic speckle index value change your maximum excursion with 
+the variation of sampling frequency because this affect directly the time integration 
 (exposition time) of camera.
+We highlight the importance of knowing  the frequency band of analyzed phenomenon, 
+to thus can choose the appropriate sampling frequency, 
+being recommendable to use the minimal sampling frequency possible
+to get an acceptable maximum excursion, 
+and an illumination level in the images with good signal-noise relation.
+
 \end{abstract}
@@
 \begin{keyword}
-Frequency sampling \sep
+Sampling frequency \sep
 Dynamic speckle index \sep 
@@
 %1) Anuncie o tema e o problema do artigo (forma de pergunta + definiçoes)
+The dynamic laser speckle analysis is  an important
+study topic\cite{catalano2019viability,rivera2019sound,gonzalez2018diode,Silva2018,braga2017dynamic} 
+to determine the  activity level of biological materials. 
+The importance of technical aspects of dynamic laser speckle analysis,
+as the stability of laser illumination level has been  analyzed, 
+and It was studded the effect of illumination instability over an index value \cite{gonzalez2018diode},
+as the absolute values of the differences \cite{cardoso2014,rivera2017selection}, and
+It  was showed the dependence between the index value and the illumination level.
 
-The dynamic speckle analysis over biological samples has become  currently  an important
-study topic\cite{catalano2019viability,rivera2019sound,gonzalez2018diode,Silva2018,braga2017dynamic} 
-to determine the level of biological activity. 
-The importance of technical aspects of dynamic speckle analysis,
-as the stability of laser illumination level, was analized \cite{gonzalez2018diode}; 
-and was showed as indexes as
-the absolute values of the differences \cite{cardoso2014,rivera2017selection} are affected in your values
-by the variation of illumination level. Thus, It is necessary analyze the effect
-of technical parameters that affect the perceived illumination level; In these sense
-analyze the effect of sampling frequency in a dynamic speckle analysis
+%3) Resgate a problematica( Importancia do problema de pesquisa - extenda primer passo)
+Thus, 
+It is necessary analyze the effect of technical parameters that affect the perceived illumination level; 
+in these sense,
+we analyze the effect of sampling frequency, 
+and consequently the exposure time, in a dynamic laser speckle analysis
+that use: the absolute value of the differences index, 
+the temporal speckle standard deviation index and the temporal speckle mean index \cite{Nothdurft:05}.
+
+%4) Relevancia do artigo(importancia para outros del artigo publicado)
+Knowing the effect of sampling frequency over an index value,
+a researcher will be able to have a criteria to choose the appropriate sampling frequency 
+for a certain study phenomenon. Thus,
+ optimizing resources when choosing the hardware specification in a system setup; 
+being in this case, the limitations relatives to illumination level and signal-noise relation in the study sample.
+
+%5) Anuncie a hipotesis
+For this purpose, we show that give a dynamic speckle test, exist a appropriate frequency band
+to choose the sampling frequency, and that to use high values of this parameters
+may to have unintended consequences on the index value, 
+as the decrease of the excursion between two activity levels, given a determinate index value. 
+by other side we known by other work \cite{Nothdurft:05}; 
+that decreasing the sampling frequency, and consequently increase the exposure time,
+reduce the image contrast in a processed test and consequently limit the possibility
+of to get information about the inside of the sample.
+
+%6) Anuncie os objetivos (receita pra demostrar a h.)
+To be able to demonstrate the existence of this appropriate frequency band,
+we will perform two types of tests, in the first we analyze a  ink drying process along the time; and
+the second test analyze, in a determinate time, the activity state of a corn seed, with 3 days of germination.
+In both case are used 4 different sampling frequencies, 
+and are compared the behavior of used speckle indexes.
 
 %2) Exponha qual será o percurso (defina seçoes)
-%3) Resgate a problematica( Importancia do problema de pesquisa - extenda primer passo)
-%4) Relevancia do artigo(importancia para outros del artigo publicado)
-%5) Anuncie a hipotesi
-%6) Anuncie os objetivos (receita pra demostrar a h.)
+In the next section we describe how the speckle images were acquired and the setup used to analyze them; 
+all theoretical definitions, necessary to understand the analysis, will shown in the Section 3;
+numerical results of the analysis  are presented in Section 4, and
+an analysis of the results is reported in the Section 5; finally, we present our
+conclusion in the Section 6.
 
@@
 \label{subsec:expositiontime}
-The acquisition time,  frame per seconds ($fps$) or sampling frequency ($F_s$), 
-in the camera Marlin F-033 will be calculated in the 
- Table \ref{table:1}, where we can see, the shutter register value ($Shutter$), 
+The sampling frequency ($F_s$) or acquisition time, frame per seconds ($fps$), 
+in the camera Marlin F-033 is calculated in the 
+ Table \ref{table:1}, 
+\begin{table}[h!]
+\centering
+\begin{tabular}{||c c c c c||} 
+ \hline
+ $Shutter$ &  $Base$ [$\mu s$] & $Offset$ [$\mu s$] & $E$ [$ms$] & $F_s$ [$fps$]\\ [0.5ex] 
+ \hline\hline
+ 3332  & 20  & 12  & 66.652  & 15.003  \\ 
+ 1665  & 20  & 12  & 33.312  & 30.019  \\ 
+ 1110  & 20  & 12  & 22.212  & 45.021  \\ 
+ 832   & 20  & 12  & 16.652  & 60.053  \\ [1ex] 
+ \hline
+\end{tabular}
+\caption{Exposition time and sampling frequency}
+\label{table:1}
+\end{table}
+where we can see the 4 sampling frequencies used in the tests, the shutter register value ($Shutter$), 
 time base register value ($Base$),
@@
 that is the time between end and start of a photography.
-\begin{table}[h!]
-\centering
-\begin{tabular}{||c c c c c||} 
- \hline
- $Shutter$ &  $Base$ [$\mu s$] & $Offset$ [$\mu s$] & $E$ [$ms$] & $F_s$ [$fps$]\\ [0.5ex] 
- \hline\hline
- 3332  & 20  & 12  & 66.652  & 15.003  \\ 
- 1665  & 20  & 12  & 33.312  & 30.019  \\ 
- 1110  & 20  & 12  & 22.212  & 45.021  \\ 
- 832   & 20  & 12  & 16.652  & 60.053  \\ [1ex] 
- \hline
-\end{tabular}
-\caption{Exposition time and sampling frequency}
-\label{table:1}
-\end{table}
+In all cases the exposure time is much bigger than $Offset$, so we can approximate
+that $F_s\approx 1/Exposure$.
 
@@
 \label{subsec:data1}
- This data package analyze a drying ink process, 
- where images data packages are taken at the times
+ This set of data  analyze a drying ink process, 
+ where group of images (data package) are taken at the times
  $\{0,$ $1,$ $2,$ $3,$ $4,$ $5,$ $6,$ $7,$ $8,$ $9,$ $10\}$ min. 
- In each time, the package
+ In each time, a package
  has 512 images of 147 pixels of height and 166 pixels of width.
- They were use 4 different sampling frequencies to the images in each package,
+ They were use 4 different sampling frequencies to take the images,
  being these frequencies $15$, $30$, $45$ and $60$ hz.
@@
  This data package analyze the activity of a corn seed with 3 days of germination. 
- In this point, 
- They are taken 4 image data packages with different sampling frequencies to each package,
+ In this seed are taken 4 image data packages with different sampling frequencies to each package,
  being these frequencies $15$, $30$, $45$ and $60$ hz.
@@
 \label{subsec:test1}
-The Fig. \ref{fig:test1} represents the data analysis method, acquired at a 
-sampling frequency of $F_s$, 
-with the characteristic seen in the Section \ref{subsec:data1},
+The Fig. \ref{fig:test1} represents the data analysis method, 
+to given  $F_s$ sampling frequency, 
+with a sample of the characteristic described in the Section \ref{subsec:data1}.
 \begin{figure}[ht!]
@@
 \end{figure}
-where, $P(t)$ is an image data package at the time $t$ minutes, 
-being that this package has $N$ images and $M$ pixels, where $P_{n,m}(t)$ 
+Where, $P(t)$ is an image data package at the time $t$ minutes, 
+being that this package has $N$ images and $M$ pixels; $P_{n,m}(t)$ 
 define the $n$-th image and $m$-th pixel, for all $1 \leq n \leq N$, $1 \leq m \leq M$.
-The $MEAN$ block represents the calculus of a temporal speckle mean index from 
+The $MEAN$ block represents the calculus of a temporal speckle mean index on 
 the package $P(t)$, returning the value $MEAN(t)$, as exposed in the Section \ref{sec:mean}. 
-The $AVD$ block represents the calculus of an absolute values of the differences index from 
+The $AVD$ block represents the calculus of an absolute values of the differences index on
 the package $P(t)$, returning the value $AVD(t)$, as exposed in the Section \ref{sec:avd}. 
-The $STD$ block represents the calculus of a temporal speckle standard deviation index from 
-the package $P(t)$, returning the value $STD(t)$, as exposed in the Section \ref{sec:std}.
+The $STD$ block represents the calculus of a temporal speckle standard deviation index on 
+the package $P(t)$ or $Q(t)$, returning the value $STD(t)$ or $STDF(t)$, respectively; as exposed in the Section \ref{sec:std}.
 And finally,
@@
 According the information of the data packages, 
-we will have speckle indexes values, for each minute during 10 minutes.
+we will have speckle indexes values, for each minute, during 10 minutes.
 
@@
 We analyze this information of similar way to the seen in the Section \ref{subsec:test1},
-with the difference that is taken an data package at the time $t$ (3 days of germination)
-and a sampling frequency $F_s$.
+with the difference that is taken an data package only at the time $t$ (3 days of germination).
 
@@
 described in the Sec \ref{sec:stdb}, with a frequency band pass between $f_1(l)$ and $f_2(l)$,
-according the Eq. \ref{eq:f1f2}, where $l$ represent the band so that $1\leq l\leq L$,
+where $l$ represent the band so that $1\leq l\leq L$,
 being $L$ the quantity of analysis frequency bands; 
@@
 The temporal speckle mean index ($\mu_{m}$) \cite{Nothdurft:05} calculates the mean
-value of the illumination level to the $m$-th pixel in the package $P$, It is implemented
+value of the illumination level to the $m$-th pixel in the package $P$, and It is implemented
 with the Eq. \ref{eq:mu},
@@
 \end{equation}
-Finally, the $MEAN$ index is the mean value of all $\mu_{m}$ results,
+Finally, the $MEAN(t)$ index is the mean value of all $\mu_{m}$ results,
 as can be viewed in the Eq. \ref{eq:MEAN},
 \begin{equation}\label{eq:MEAN}
-MEAN = \sum \limits_{m=1}^{M} \frac{\mu_{m}}{M}.
+MEAN(t) = \sum \limits_{m=1}^{M} \frac{\mu_{m}}{M}.
 \end{equation}
@@
 \end{equation}
-Finally, the $AVD$ index is the mean value of all $AVD_{m}$ results,
+Finally, the $AVD(t)$ index is the mean value of all $AVD_{m}$ results,
 as can be viewed in the Eq. \ref{eq:AVD},
 \begin{equation}\label{eq:AVD}
-AVD = \sum \limits_{m=1}^{M} \frac{AVD_{m}}{M}
+AVD(t) = \sum \limits_{m=1}^{M} \frac{AVD_{m}}{M}
 \end{equation}
@@
 \end{equation}
-Finally, the $STD$ index is the mean value of all $\sigma_{m}$ results,
+Finally, the $STD(t)$ index is the mean value of all $\sigma_{m}$ results,
 as can be viewed in the Eq. \ref{eq:STD},
 \begin{equation}\label{eq:STD}
-STD = \sum \limits_{m=1}^{M} \frac{\sigma_{m}}{M}
+STD(t) = \sum \limits_{m=1}^{M} \frac{\sigma_{m}}{M}
 \end{equation}
@@
 This test shows the analyze result of an ink drying process, across 10 minutes,
-with the sampling frequency: $15$, $30$, $45$ and $60$Hz.
+using the sampling frequencies: $15$, $30$, $45$ and $60$Hz.
 
@@
 in the test showed in the Section \ref{subsec:test1},
-to each time $t$ for 4 sampling frequencies.
+to each time $t$ for the  4 sampling frequencies.
 \begin{figure}[ht!]
@@
 the sampling frequency. Remembering that this index use information in a frequency
-band between $F_s/4$ until $F_s/2$ Hz, as seen in Section \ref{sec:avd}.
+band between $F_s/4$ until $F_s/2$ Hz \cite{rivera2017selection}.
 
@@
 The Figure \ref{fig:stdraw} shows the  behavior of $STD(t)$ index, in each time $t$, 
-to 4 different sampling frequencies. Remembering that this index uses information in a frequency
-band between $0$ until $F_s/2$ Hz, as seen in Section \ref{sec:std}.
+to 4 different sampling frequencies. Remembering that this index uses information in the entire frequency
+band ($0$ until $F_s/2$ Hz), as seen in Section \ref{sec:std}.
 This index shows a different behavior across time to each sampling frequency,
@@
 of the curves with different sampling frequency; even so, It is possible to observe
-a decrease of the maximum excursion in the curve with the grow of the sampling frequency.
+a slight decrease of the maximum excursion in the curve with the grow of the sampling frequency, 
+unlike the $AVD(t)$ index.
 
@@
 of the curves with the use of sampling frequency; so, It is possible to observe a 
-grow of the maximum excursion with the grow of the sampling frequency.
+grow of the maximum excursion with the grow of the sampling frequency, like the $AVD(t)$ index.
 
@@
 This test shows the analyze result of a corn seed  with 3 days of germination,
-with the sampling frequencies: $15$, $30$, $45$ and $60$Hz.
+with images acquires using the sampling frequencies: $15$, $30$, $45$ and $60$Hz.
 
@@
 \end{figure}
-The figure shows as the index decrease your value, 
+We observe as the index decrease your value, 
 with the increment of sampling frequency in the datapack,
@@
 so that the indexes, 
-$AVD(t)$, $STD(t)$ and $STDF(t)$, 
+$STD(t)$, $AVD(t)$  and $STDF(t)$, 
 reaches the $22.2426\%$, $19.2578\%$ and $20.3541\%$ of your values, 
@@
 in different frequency bands over a package $P$, see Sec. \ref{subsec:test3}, 
-The package represents  a corn seed as in the Section \ref{subsec:data2};
+The package represents  a corn seed described in the Section \ref{subsec:data2};
 where, we have packages sampled with the frequencies: $15$, $30$, $45$ and $60$ Hz, as
@@
 these frequency bands limited on: $0$, $3.75$, $7.5$, $11.25$, $15$, $18.75$, $22.5$, $26.25$ and $30$Hz.
-So that, the package sampled in $15$hz was divided in $L=2$ frequency bands, 
-in $30$hz was divided in $L=4$ frequency bands, 
-in $45$hz was divided in $L=6$ frequency bands and finally
-in $60$hz was divided in $L=8$ frequency bands.
+So that, the package sampled at $15$hz was divided in $L=2$ frequency bands, 
+at $30$hz was divided in $L=4$ frequency bands, 
+at $45$hz was divided in $L=6$ frequency bands and finally
+at $60$hz was divided in $L=8$ frequency bands.
 
 The matrices $STDB$ are represented using a color palette, 
-that goes from dark blue to dark red color, representing of ascendant way the values
-in each pixel in all matrices. It is evident how the index values decreases with
+that goes from dark blue to dark red color, 
+representing of ascendant way the values in each pixel in all matrices, 
+as It is shown in the top of table. 
+It is evident how the index values decreases with
 the increment of frequency sampling $F_s$ in each one of 8 frequency bands, 
@@
 being the best analysis case, 
-in the sense of differentiating better places of lower and higher index, 
+in the sense of better differentiating places of lower and higher index value, 
 to a frequency sampling of $15$ hz and a frequency band between $0$ Hz and $3.75$ Hz.
@@
 How is known \cite{Nothdurft:05}, the temporal speckle mean index is related to 
-the observed illumination level in the surface of study material and correspond to zero frequency of the signal (datapack).
-Thus, we can conclude that the level of illumination, perceived by the camera, 
+the observed illumination level in the surface of study material and correspond to zero frequency of the signal (datapack);
+thus, we can conclude that the level of illumination, perceived by the camera, 
 decrease with the increment of sampling frequency. 
@@
 we can see how the use of half, of entire frequency band, causes the decrease in the values of the curves, 
-but give us considerably good values in the maximum excursion of the curve. By other side,
-in the case of ink drying process, the use of complete frequency band, 
-It returns low values of maximum excursion in the curves. 
+but give us considerably good values in the maximum excursion of the curve across the time. By other side,
+in the case of ink drying process, the use of complete frequency band ($STD(t)$ index), 
+It returns low values of maximum excursion in the curves across the time. 
 The importance of excursion in this test,
@@
 the frequency band of signal contain the frequency components with the information that you want to analyze;
-so that, the values of indexes have the greatest values and consequently a good excursion, 
+so that, the values of indexes have the greatest values and probably a good excursion, 
 when compared with an inert part of sample; 
@@
 all frequency bands, 
-the best frequency band, to the case of corn seed, is the one with the components with less frequency.
+the best frequency band, to the case of corn seed, is the one with the components with less frequency; but
+without  forget that given the $STD(t)$ index extract information of internal parts of material, and
+this information decrease jointly with the exposure time \cite{Nothdurft:05},
+we need to choose a compromise between the internal information of the sample that we need, 
+the perceived illumination level and the sampling frequency.
 
@@
 
-In this work were presented comparisons of behavior of three dynamic speckle indexes
+In this work were presented comparisons in the  behavior of three dynamic laser speckle indexes
 subject to different values of sampling frequency, thus we concluded that:
-It is important to know to choose an appropriate sampling frequency, 
+It is important to choose an appropriate sampling frequency, 
 being recommendable to use the minimal sampling frequency possible to get an acceptable maximum excursion, 
-so that the phenomenon under study to be in the analyzed frequency band.
+in index as the $AVD$ and $STDF$,
+and an illumination level in the images with good signal-noise relation,
+so that the phenomenon under study be in the analyzed frequency band.
 Finally, 

### 2019-04-04 mcode/mcode-maiz-freqfreq/func_dir_std_2freq.m
ordenand datos

@@ -20,14 +20,15 @@ function [STD MEAN AVD STDF h]=func_dir_std_2freq(DIRROOT,NUM,OUTPUT,FACTOR)
     %% To filenames: 'img1coffee.bmp', 'img2coffee,bmp', ..., 'img100coffee.bmp'
     DATA = datapack(DIR,'%d',1,512,'bmp');
     %DATA=DATA(180:(end-100),150:(end-150),:);
-    
+
     %% pkg load image
-    %% FF = fspecial("average", 3);
+    %% FF = fspecial("average", 3);    
 
     [C D E]=stdcont(DATA,'off');
     %% D = imfilter(D, FF);
     %% E = imfilter(E, FF);
 
+    %DMAX=0;
     imagesc(E); title('MEAN')  
     colormap(jet);
     colorbar;
@@ -40,7 +41,6 @@ function [STD MEAN AVD STDF h]=func_dir_std_2freq(DIRROOT,NUM,OUTPUT,FACTOR)
     FileName=fullfile(OUTPUT,[num2str(NUM) 'fps'],'STD.eps');
     print(gcf,FileName,'-depsc')
 
-    DMAX=0;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     for II=1:N   
         [DATAF DATA1] = firfilterbank(DATA,H{II},'MODE0');
@@ -48,13 +48,13 @@ function [STD MEAN AVD STDF h]=func_dir_std_2freq(DIRROOT,NUM,OUTPUT,FACTOR)
 
         [C D E]=stdcont(DATAF,'off');
 
-        %D = imfilter(D, FF);
+        %% D = imfilter(D, FF);
 
         imagesc(D);  
         colormap(jet);
-        if II==1
+        %if II==1
             DMAX=max(max(D));
-        endif
+        %endif
 
         NCOLORS=256;
         Dind = gray2ind(D/DMAX, NCOLORS);

### 2019-09-02 article/article_1.tex
artigo coregido

--- 2019-03-25 article/article_1.tex
@@
 
-\title{Importance of Sampling Frequency in the Dynamic Speckle Analysis}
+\title{Sampling Frequency in the Dynamic Speckle Analysis}
 %\tnotetext[mytitlenote]{Fully documented templates are available in the 
@@
 % Group authors per affiliation:
-\author{------ ----- -----}
-\author{------ ----- -----}
+\author{Rivera, F. P.}
+\author{Pe\~na, R. G.}
+\author{Braga, R. A.}
 
 \address{University Federal of Lavras, Lavras, Brazil}
-\fntext[myfootnote2]{201518201@posgrad.ufla.br}
-\fntext[myfootnote1]{robertobraga@deg.ufla.br }
+%\fntext[myfootnote2]{201518201@posgrad.ufla.br}
+%\fntext[myfootnote1]{robertobraga@deg.ufla.br }
 %
@@
 In this article, we show as the variation of sampling frequency, 
-in a dynamic speckle analysis, affect the value of some dynamic speckle index, 
-in this case: the absolute value of the differences index, the temporal 
+in a dynamic speckle analysis, affects the value of some dynamic speckle index, 
+to the cases of the absolute value of the differences index, the temporal 
 speckle standard deviation index and the temporal 
 speckle mean index.
-we show that  the dynamic speckle index value decrease your maximum excursion with 
-the grow of sampling frequency because this affect directly the time integration 
+We show that  the dynamic speckle index value change the maximum excursion with 
+the variation of sampling frequency, affected directly by the time integration 
 (exposition time) of camera.
+We highlight the importance of knowing  the frequency band of analyzed phenomenon, 
+in order to choose the appropriate sampling frequency, 
+being recommendable to use the minimal sampling frequency possible
+to get an acceptable maximum excursion, 
+and an illumination level with good signal-noise ratio.
+
 \end{abstract}
@@
 %1) Anuncie o tema e o problema do artigo (forma de pergunta + definiçoes)
+The dynamic laser speckle analysis is  an important
+study topic\cite{catalano2019viability,rivera2019sound,gonzalez2018diode,Silva2018,braga2017dynamic} 
+to determine the  activity level of biological materials. 
+The importance of technical aspects of dynamic laser speckle analysis,
+as the stability of laser illumination level has been  analyzed \cite{gonzalez2018diode}, 
+and it was analyzed the effect of illumination instability over an index value \cite{gonzalez2018diode},
+such as the absolute values of the differences \cite{cardoso2014,rivera2017selection}.
+It  was showed the dependence between the index value and the illumination level.
 
-The dynamic speckle analysis over biological samples has become  currently  an important
-study topic\cite{catalano2019viability,rivera2019sound,gonzalez2018diode,Silva2018,braga2017dynamic} 
-to determine the level of biological activity. 
-The importance of technical aspects of dynamic speckle analysis,
-as the stability of laser illumination level, was analized \cite{gonzalez2018diode}; 
-and was showed as indexes as
-the absolute values of the differences \cite{cardoso2014,rivera2017selection} are affected in your values
-by the variation of illumination level. Thus, It is necessary analyze the effect
-of technical parameters that affect the perceived illumination level; In these sense
-analyze the effect of sampling frequency in a dynamic speckle analysis
+%3) Resgate a problematica( Importancia do problema de pesquisa - extenda primer passo)
+Thus, 
+it is necessary analyze the effect of technical parameters that affect the perceived illumination level; 
+in these sense,
+we analyze the effect of sampling frequency, 
+and consequently the time exposure, in a dynamic laser speckle analysis
+that use: the absolute value of the differences index, 
+the temporal speckle standard deviation index and the temporal speckle mean index \cite{Nothdurft:05}.
+
+%4) Relevancia do artigo(importancia para outros del artigo publicado)
+Knowing the effect of sampling frequency over an index value,
+a researcher will be able to have a criteria to choose the appropriate sampling frequency 
+for a certain monitored phenomenon. 
+% Thus,
+% optimizing resources when choosing the hardware specification in a system setup; 
+% being in this case, the limitations relatives to illumination level and signal-noise relation in the study sample.
+
+%5) Anuncie a hipotesis
+For this purpose, we show that given a dynamic speckle test, exists an appropriate frequency band
+to the sampling frequency. High values of sampling rate may cause unintended consequences on the index value, 
+such as the decrease of the excursion between two activity levels, given a determinate index value. 
+In turn, decreasing the sampling frequency promoted by the increasing of the exposure time,
+will cause a reduction of the temporal speckle contrast,
+ and consequently limit the possibility  to get information from the sample.
+
+%6) Anuncie os objetivos (receita pra demostrar a h.)
+To be able to demonstrate the existence of this appropriate frequency band,
+we will perform two types of tests; in the first, we analyzed an ink drying process along the time; and in
+the second, we tested the activity state of a corn seed, with 3 days of germination.
+In both cases, were used four different sampling rates, 
+and was compared the behavior of speckle indexes.
 
 %2) Exponha qual será o percurso (defina seçoes)
-%3) Resgate a problematica( Importancia do problema de pesquisa - extenda primer passo)
-%4) Relevancia do artigo(importancia para outros del artigo publicado)
-%5) Anuncie a hipotesi
-%6) Anuncie os objetivos (receita pra demostrar a h.)
+In the next section we describe how the speckle images were acquired and the setup used to analyze them; 
+all theoretical definitions, necessary to understand the analysis, will shown in the Section 3;
+numerical results of the analysis  are presented in Section 4, and
+an analysis of the results is reported in the Section 5; finally, we present our
+conclusion in the Section 6.
 
@@
 
-\subsection{Exposure time of the camera}
+\subsection{Time exposure of the camera}
 \label{subsec:expositiontime}
-The acquisition time,  frame per seconds ($fps$) or sampling frequency ($F_s$), 
-in the camera Marlin F-033 will be calculated in the 
- Table \ref{table:1}, where we can see, the shutter register value ($Shutter$), 
-time base register value ($Base$),
-exposure time ($Exposure$),
-exposure time offset ($Offset$) and
-effective exposure time ($E$); so that 
-\begin{equation}
-Exposure= Shutter \times Base,
-\end{equation}
-\begin{equation}
-\frac{1}{F_s}=E= Exposure + Offset.
-\end{equation}
-Where,  $F_s$ is calculated in relation to the  $E$; being that,
-the $Exposure$ represent the photography integration time and $E$ the effective time
-between photographs; 
-the difference between these two exposures arise from $Offset$ time, 
-that is the time between end and start of a photography.
+The sampling frequency ($F_s$) or acquisition time in frames per second ($fps$), 
+in the camera Marlin F-033 is obtained using the 
+ Table \ref{table:1}, 
 \begin{table}[h!]
@@
 \end{table}
+where we can see the 4 sampling frequencies that will be used in the tests;
+these values were obtained using  
+the shutter register value ($Shutter$), 
+the time base register value ($Base$),
+the exposure time offset ($Offset$) and
+the effective exposure time ($E$);
+ so that the exposure time ($Exposure$),
+\begin{equation}
+Exposure= Shutter \times Base,
+\end{equation}
+\begin{equation}
+\frac{1}{F_s}=E= Exposure + Offset.
+\end{equation}
+Where,  $F_s$ is calculated in relation to $E$; being that,
+the $Exposure$ represent the photography integration time and $E$ the effective time
+between photographs; 
+the difference between these two exposures arise from $Offset$ time, 
+that is the time between end and start of a photography.
+In all cases the exposure time is much bigger than $Offset$; so, we can approximate
+that $F_s\approx 1/Exposure$.
 
-\subsection{Data packages in the ink drying process}
+\subsection{Data-packages of ink drying process}
 \label{subsec:data1}
- This data package analyze a drying ink process, 
- where images data packages are taken at the times
+ This data set comes from an ink drying process, 
+ where groups of images (data package) are taken at the times
  $\{0,$ $1,$ $2,$ $3,$ $4,$ $5,$ $6,$ $7,$ $8,$ $9,$ $10\}$ min. 
- In each time, the package
- has 512 images of 147 pixels of height and 166 pixels of width.
- They were use 4 different sampling frequencies to the images in each package,
- being these frequencies $15$, $30$, $45$ and $60$ hz.
+ In each time, an acquired package  has 512 images of 147 pixels of height and 166 pixels of width.
+4 different sampling rates were used to take the images,
+ being these rates $15$, $30$, $45$ and $60$ hz.
 
-\subsection{Data package of the activity analysis in corn seed}
+\subsection{Data-package of maize seed germination}
 \label{subsec:data2}
- This data package analyze the activity of a corn seed with 3 days of germination. 
- In this point, 
- They are taken 4 image data packages with different sampling frequencies to each package,
- being these frequencies $15$, $30$, $45$ and $60$ hz.
- Each package has 512 images of $15$ pixels of height and $15$ pixels of width.
+ This data-package has the speckle pattern of a maize seed with 3 days of germination,
+ where four data-packages with different sampling rates ( $15$, $30$, $45$ and $60$ hz)  
+were built.
+Each package have 512 images of $15$ pixels of height and $15$ pixels of width.
 
@@
 \label{subsec:test1}
-The Fig. \ref{fig:test1} represents the data analysis method, acquired at a 
-sampling frequency of $F_s$, 
-with the characteristic seen in the Section \ref{subsec:data1},
+Fig. \ref{fig:test1} represents the data analysis method in an ink drying process, 
+to a $F_s$ sampling rate.
 \begin{figure}[ht!]
@@
 \end{figure}
-where, $P(t)$ is an image data package at the time $t$ minutes, 
-being that this package has $N$ images and $M$ pixels, where $P_{n,m}(t)$ 
+Where, $P(t)$ is an data-package with  images at the time $t$ minutes; 
+this package has $N$ images and $M$ pixels; $P_{n,m}(t)$ 
 define the $n$-th image and $m$-th pixel, for all $1 \leq n \leq N$, $1 \leq m \leq M$.
-The $MEAN$ block represents the calculus of a temporal speckle mean index from 
-the package $P(t)$, returning the value $MEAN(t)$, as exposed in the Section \ref{sec:mean}. 
-The $AVD$ block represents the calculus of an absolute values of the differences index from 
-the package $P(t)$, returning the value $AVD(t)$, as exposed in the Section \ref{sec:avd}. 
-The $STD$ block represents the calculus of a temporal speckle standard deviation index from 
-the package $P(t)$, returning the value $STD(t)$, as exposed in the Section \ref{sec:std}.
+The $MEAN$ block represents the calculation of temporal speckle mean index on 
+the package $P(t)$, returning the value $MEAN(t)$. 
+The $AVD$ block represents the calculation of  absolute values of the differences index on
+the package $P(t)$, returning the value $AVD(t)$. 
+The $STD$ block represents the calculation of the temporal speckle standard deviation index on 
+the package $P(t)$ or $Q(t)$, returning the value $STD(t)$ or $STDF(t)$, respectively.
 And finally,
-the block $HPF$ represents a digital finite impulse response ``high-pass filter'' 
-with order $40$ and cut-off at $0.25F_s$ and this block filter the $P(t)$ package and return $Q(t)$,
-that causes to have at end of path the $STDF(t)$ index value.
-According the information of the data packages, 
-we will have speckle indexes values, for each minute during 10 minutes.
+the block \hyperref[sec:stdf]{$HPF$} represents a digital finite impulse response ``high-pass filter'' 
+with order $40$ and cut-off at $0.25F_s$; this block filter the $P(t)$ package and return $Q(t)$,
+leading this result to a $STD$ block to finally obtain the $STDF(t)$ index value.
+According to the information of the data packages, 
+we will have speckle indexes values, for each minute, during 10 minutes.
 
-\subsection{Test 2: Activity analysis in corn seed}
+\subsection{Test 2: Maize seed germination}
 \label{subsec:test2}
-The activity analysis of a corn seed, 
-uses the information of data package seen in the Section \ref{subsec:data2}.
-We analyze this information of similar way to the seen in the Section \ref{subsec:test1},
-with the difference that is taken an data package at the time $t$ (3 days of germination)
-and a sampling frequency $F_s$.
+The speckle activity of a maize seed
+was analyzed in a similar way to the ink drying, seen in the Section \ref{subsec:test1}, 
+with the difference that only one data-package was taken at the time $t$, equal to 3 days of germination.
 
@@
 The Fig. \ref{fig:test3} represents the frequency band analysis method of data package $P$, 
-acquired  with a sampling frequency of $F_s$. This package pass through the $BPF$ block
-described in the Sec \ref{sec:stdb}, with a frequency band pass between $f_1(l)$ and $f_2(l)$,
-according the Eq. \ref{eq:f1f2}, where $l$ represent the band so that $1\leq l\leq L$,
-being $L$ the quantity of analysis frequency bands; 
-thus, we obtaining the  $R$ package (a filtered version of $P$). Later, It is processed 
-a $\sigma$ block, where It is calculate the $\sigma_{m}$ value to each pixel in the package $R$,
+acquired  with a sampling rate of $F_s$. This package is the input of many band pass filter (\hyperref[sec:stdb]{$BPF$}) blocks,
+described in the Sec \ref{sec:stdb}, these band pass filter have cut-off frequencies between $f_1(l)$ and $f_2(l)$,
+where $l$ indicates the current band, so that $1\leq l\leq L$;
+being $L$ the total number of analysis frequency bands; 
+thus, we obtained the  $R_l$ package (a filtered version of $P$). $R_l$ was processed 
+by a $\sigma$ block, where it is calculated the $\sigma_{m}$ value to each pixel in the package $R_l$,
 as described in the Sec \ref{sec:std}. Finally, 
-an image is obtained and It is designed with the variable $STDB$.
+an image is obtained and it is named as the variable $STDB_l$.
 \begin{figure}[ht!]
@@
 
-In the next subsections we use the variable $P$ to define $P(t)$ in any time $t$.
+In the next subsections we use the variable $P$ to define $P(t)$ in any time $t$;
+thus, $P$ represents a data collection of images in any time.
 
@@
 
-The temporal speckle mean index ($\mu_{m}$) \cite{Nothdurft:05} calculates the mean
-value of the illumination level to the $m$-th pixel in the package $P$, It is implemented
-with the Eq. \ref{eq:mu},
+The temporal speckle mean index ($\mu_{m}$) \cite{Nothdurft:05} gives the mean
+value of the illumination level to the $m$-th pixel in the package $P$, 
+and it was  implemented as presented in Eq. \ref{eq:mu}, where $N$ is the number of image in the package,
 \begin{equation}\label{eq:mu}
@@
 \end{equation}
-Finally, the $MEAN$ index is the mean value of all $\mu_{m}$ results,
+Finally, the $MEAN(t)$ index is the spatial mean value of all $\mu_{m}$ results,
 as can be viewed in the Eq. \ref{eq:MEAN},
 \begin{equation}\label{eq:MEAN}
-MEAN = \sum \limits_{m=1}^{M} \frac{\mu_{m}}{M}.
+MEAN(t) = \sum \limits_{m=1}^{M} \frac{\mu_{m}}{M}.
 \end{equation}
@@
 
-The Absolute Values of the Differences ($AVD_{m}$) \cite{cardoso2014,rivera2017selection} calculates the mean
-value of the absolute differences in the illumination level of the $m$-th pixel in the package $P$, It is implemented
-with the Eq. \ref{eq:avd0},
+The Absolute Values of the Differences ($AVD_{m}$) \cite{cardoso2014,rivera2017selection} gives the mean
+value of the absolute differences in the illumination level of the $m$-th pixel in the package $P$, it was  implemented
+by Eq. \ref{eq:avd0},
 \begin{equation}\label{eq:avd0}
@@
 \end{equation}
-Finally, the $AVD$ index is the mean value of all $AVD_{m}$ results,
+Finally, the $AVD(t)$ index is the spatial mean value of all $AVD_{m}$ results,
 as can be viewed in the Eq. \ref{eq:AVD},
 \begin{equation}\label{eq:AVD}
-AVD = \sum \limits_{m=1}^{M} \frac{AVD_{m}}{M}
+AVD(t) = \sum \limits_{m=1}^{M} \frac{AVD_{m}}{M}
 \end{equation}
@@
 
-The temporal speckle standard deviation index ($\sigma_{m}$) \cite{Nothdurft:05} calculates the standard deviation
-value of the illumination level to the $m$-th pixel in the package $P$, It is implemented
+The temporal speckle standard deviation index ($\sigma_{m}$) \cite{Nothdurft:05} gives the standard deviation
+value of the illumination level to the $m$-th pixel in the package $P$, it was implemented
 with the Eq. \ref{eq:sigma},
@@
 \end{equation}
-Finally, the $STD$ index is the mean value of all $\sigma_{m}$ results,
+Finally, the $STD(t)$ index is the spatial mean value of all $\sigma_{m}$ results,
 as can be viewed in the Eq. \ref{eq:STD},
 \begin{equation}\label{eq:STD}
-STD = \sum \limits_{m=1}^{M} \frac{\sigma_{m}}{M}
+STD(t) = \sum \limits_{m=1}^{M} \frac{\sigma_{m}}{M}
 \end{equation}
@@
 
-The high-pass filter ($HPF$) block It is implemented with a finite impulse 
+The high-pass filter ($HPF$) block was implemented (Fig. \ref{fig:test1}) with a finite impulse 
 response ($FIR$)\cite{saramaki1993finite} filter
 of order 40 and cut-off at $0.25F_s$. 
-The 41 values in the filter are represented with $h(i)$, for all $0 \leq i\leq 40$ and zero in others cases, so that
-if we send a data package $P$ through the $HPF$ block we obtain a data package $Q$,
+The 41 values in the filter are represented with $h(i)$, for all $0 \leq i\leq 40$, with zero in others cases.
+Thus, a data package $P$ as input of the $HPF$ block gives us as result, a data package $Q$,
 as can be seen in the Eq. \ref{eq:fir},
@@
 
-The band-pass filter ($BPF$) block, 
-It is implemented similarly as the see in Sec. \ref{sec:stdf}, 
+The band-pass filter ($BPF$) block  is implemented (Fig. \ref{fig:test3}) similarly as the \hyperref[sec:stdf]{$HPF$} block, 
  with  a $FIR$ filter of order 40 but with a cut-off in $f_1(l)$ and $f_2(l)$, 
@@
 \end{equation}
-representing $l$, for all $1 \leq l \leq L$, the $l$-th band of $L$ parts; so that each band has $\frac{F_s}{2L}$ Hz.
-The filter is represented with $g(i)$, for all $0 \leq i\leq 40$ and zero in others cases, so that
-if we send a data package $P$ through the $BPF$ block we obtain a data package $R$,
+representing $l$, for all $1 \leq l \leq L$, the $l$-th band of $L$ bands; each band has $\frac{F_s}{2L}$ Hz.
+The filter is represented with $g(i)$, for all $0 \leq i\leq 40$, with zero in others cases. 
+Thus, a data package $P$ as input of the $BPF$ block gives us as result, a data package $R$,
 as can be seen in the Eq. \ref{eq:firb},
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Result of test 1}
+\subsection{Test 1: ink drying process}
 \label{subsec:resulttest1}
-This test shows the analyze result of an ink drying process, across 10 minutes,
-with the sampling frequency: $15$, $30$, $45$ and $60$Hz.
+This test shows the analysis result of an ink drying process, during 10 minutes,
+using the sampling rates: $15$, $30$, $45$ and $60$Hz.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The Figure \ref{fig:MEANtest1} analyze the $MEAN(t)$ index,
+Figure \ref{fig:MEANtest1} presents the $MEAN(t)$ index,
 in the test showed in the Section \ref{subsec:test1},
-to each time $t$ for 4 sampling frequencies.
+to each time $t$ for the  4 sampling rates.
 \begin{figure}[ht!]
@@
 \end{figure}
-It easy to see as the value of index has a monotonous 
-behavior over time. By other side the values in the curves decreases in proportion with 
-the grow of sampling frequency.
+It can be seen that, 
+the value of index has a monotonous behavior over time. 
+By other side the values in the curves decreases in proportion with 
+the grow of sampling rate.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The Figure \ref{fig:AVDtest1} shows the result of analysis explained in the 
+Figure \ref{fig:AVDtest1} shows the result of analysis explained in the 
 Section \ref{subsec:test1} about the $AVD(t)$ index.
@@
 The Figure \ref{fig:avdraw} shows the $AVD(t)$ index, in each time $t$, 
-to 4 sampling frequencies, showing a different behavior across time in each sampling frequency,
-so that, the value of the index in all  the curve decreases in proportion with 
-the grow of sampling frequency. By other side,
-the Figure \ref{fig:avdnorm} shows a normalized version of $AVD(t)$ index, 
+to 4 sampling rates, showing a different behavior in time to each sampling rate,
+so that, the value of the index in all  curves, decreases in proportion with 
+the grow of sampling rate. By other side,
+Figure \ref{fig:avdnorm} shows a normalized version of $AVD(t)$ index, 
 so that the maximum value of curves have an unit value; thus,
-It is easy to see that the maximum excursion of the curve is greater when decrease
-the sampling frequency. Remembering that this index use information in a frequency
-band between $F_s/4$ until $F_s/2$ Hz, as seen in Section \ref{sec:avd}.
+it can be seen that, the maximum excursion of the curve is greatest when 
+the sampling rate decrease. Remembering that this index uses information from a frequency
+band between $F_s/4$ until $F_s/2$ Hz \cite{rivera2017selection}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The Figure \ref{fig:STDtest1} analyze the $STD(t)$ index in the test showed in the 
+Figure \ref{fig:STDtest1} presents the $STD(t)$ index in the test showed in the 
 Section \ref{subsec:test1}.
@@
 The Figure \ref{fig:stdraw} shows the  behavior of $STD(t)$ index, in each time $t$, 
-to 4 different sampling frequencies. Remembering that this index uses information in a frequency
-band between $0$ until $F_s/2$ Hz, as seen in Section \ref{sec:std}.
-This index shows a different behavior across time to each sampling frequency,
-so that, the value of the index in each time of curve decreases in proportion with 
-the grow of sampling frequency. By other side,
-the Figure \ref{fig:stdnorm} shows a normalized version of $STD(t)$ index;
+to 4 different sampling rates. Remembering that this index uses information in the entire frequency
+band ($0$ until $F_s/2$ Hz), as seen in Section \ref{sec:std}.
+This index shows a different behavior in time to each sampling frequency,
+so that, the value of the index in each time  decreases in proportion with 
+the grow of sampling rate. By other side,
+Figure \ref{fig:stdnorm} shows a normalized version of $STD(t)$ index;
 being the unit, the maximum value of curves; thus,
-It is easy to see that exist a small difference between the maximum excursion 
-of the curves with different sampling frequency; even so, It is possible to observe
-a decrease of the maximum excursion in the curve with the grow of the sampling frequency.
+it can be seen that exists a small difference between the maximum excursion 
+of the curves with different sampling rates; even so, it is possible to observe
+a slight decrease of the maximum excursion in the curve with the grow of the sampling rate, 
+unlike the $AVD(t)$ index.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The Figure \ref{fig:STDFtest1}, analyze the $STDF(t)$ index, in the test showed in the 
+Figure \ref{fig:STDFtest1}, presents the $STDF(t)$ index, in the test showed in the 
 Section \ref{subsec:test1}.
@@
 \end{figure}
-The Figure \ref{fig:stdfraw} shows the behavior $STDF(t)$ index, in each time $t$, 
-to 4 different sampling frequencies. Remembering that this index uses filtered 
-information of datapack, so that your frequency
-band is between $F_s/4$ and $F_s/2$ Hz, of similar way of $AVD(t)$ index but with
-different order filter, as seen in Section \ref{sec:stdf}.
+Figure \ref{fig:stdfraw} shows the behavior $STDF(t)$ index, in each time $t$, 
+to 4 different sampling rates. Remembering that this index uses filtered 
+information of datapack, so that the frequency
+band is between $F_s/4$ and $F_s/2$ Hz. 
+% of similar way of $AVD(t)$ index but with different order filter, as seen in Section \ref{sec:stdf}.
 This index shows monotone decreasing behavior in time, where we observe 
-a different behavior across time to each different sampling frequency;
-so that, the value of the index in each time of curve decreases in proportion with 
-the grow of sampling frequency. By other side,
-the Figure \ref{fig:stdfnorm} shows a normalized version of $STDF(t)$ index;
+a different behavior in time to each different sampling rate;
+so that, the value of the index in each time decreases in proportion with 
+the grow of sampling rate. By other side,
+Figure \ref{fig:stdfnorm} shows a normalized version of $STDF(t)$ index;
 being the unit, the maximum value of curves; thus,
-It is easy to see that exist a considerable difference between the maximum excursion 
-of the curves with the use of sampling frequency; so, It is possible to observe a 
-grow of the maximum excursion with the grow of the sampling frequency.
+it can be seen that exists a considerable difference between the maximum excursion 
+of the curves with the use of sampling frequency; so, it is possible to observe a 
+grow of the maximum excursion when the sampling rate decrease, like the $AVD(t)$ index.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Result of test 2}
+\subsection{Test 2: maize seed germination}
 \label{subsec:resulttest2}
 
-This test shows the analyze result of a corn seed  with 3 days of germination,
-with the sampling frequencies: $15$, $30$, $45$ and $60$Hz.
+This test shows the result of analyze a corn seed  with 3 days of germination,
+the images were taken using the sampling rates: $15$, $30$, $45$ and $60$Hz.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The Figure \ref{fig:MEANtest2} shows the $MEAN(t)$ index,
-in the test described in the Section \ref{subsec:test2};
+Figure \ref{fig:MEANtest2} shows the $MEAN(t)$ index,
+decreasing its value
+%in the test described in the Section \ref{subsec:test2};
 \begin{figure}[ht!]
@@
 \end{figure}
-The figure shows as the index decrease your value, 
-with the increment of sampling frequency in the datapack,
-so that between $15$ Hz until $60$ Hz, the index value reaches the $20.137\%$ of your value.
+%We observe as the index decrease your value, 
+with the increment of sampling frequency, %in the datapack,
+where from %so that between 
+$15$ Hz to $60$ Hz, the index value reached the $20.137\%$ of its value.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The Figure \ref{fig:INDEXtest2} shows the $AVD(t)$, $STD(t)$ and $STDF(t)$ indexes,
-in the test described in the Section \ref{subsec:test2};
+Figure \ref{fig:INDEXtest2} shows the $AVD(t)$, $STD(t)$ and $STDF(t)$ indexes,
+with the same behavior that the presented by $MEAN$ index.
+%in the test described in the Section \ref{subsec:test2};
 \begin{figure}[ht!]
@@
     \includegraphics[width=0.5\textwidth]{FPS_Semilla_3_3diasALL.eps}
-    \caption{$AVD(t)$, $STD(t)$ and $STDF(t)$ indexes values in the germinated corn seed.}\label{fig:INDEXtest2}
+    \caption{$AVD(t)$, $STD(t)$ and $STDF(t)$ indexes values in the germinated maize seed.}\label{fig:INDEXtest2}
 \end{figure}
-The similar way that in the Figure \ref{fig:MEANtest2},
-the index decrease your value with the grow of $F_s$,
-so that the indexes, 
-$AVD(t)$, $STD(t)$ and $STDF(t)$, 
-reaches the $22.2426\%$, $19.2578\%$ and $20.3541\%$ of your values, 
-respectively.
+%The similar way that in the Figure \ref{fig:MEANtest2},
+%the index decrease your value with the grow of $F_s$,
+%so that the indexes, $STD(t)$, $AVD(t)$  and $STDF(t)$, 
+%reaches the $22.2426\%$, $19.2578\%$ and $20.3541\%$ of your values, 
+%respectively.
+The decreasing of the activity observed are related to the increase of $F_s$
+where $STD$, $AVD$ and $STDF$ presented respectively degrowth values of $22.2426\%$
+ $19.2578\%$ and $20.3541\%$.
+%to highest $F_s$ if compared to the lowest $F_s$.
 
-\subsection{Result of test 3}
+\subsection{Test 3: frequency band activity analysis}
 \label{subsec:resulttest3}
-The Table \ref{table:2} shows the result of calculating the $STDB$ image
-in different frequency bands over a package $P$, see Sec. \ref{subsec:test3}, 
-The package represents  a corn seed as in the Section \ref{subsec:data2};
-where, we have packages sampled with the frequencies: $15$, $30$, $45$ and $60$ Hz, as
-can be seen in the first column of table.
+Table \ref{table:2} shows the 
+%result of calculating the 
+$STDB$ image in different frequency bands 
+of maize seed,
+%over a package $P$, see Sec. \ref{subsec:test3}, 
+%the package represents  a corn seed described in the Section \ref{subsec:data2};
+%where, we have packages sampled 
+using 4 different sampling rates: $15$, $30$, $45$ and $60$ Hz, as
+can be seen in the first column of the table.
 
@@
 \end{table}
-In the other columns we can see the results of until $8$ frequency bands of package $P$,
-these bands are represented in the first line of table, were $l$ indicates the position of frequency band
-in crescent order relative to the frequency components. Thus, we have 
-these frequency bands limited on: $0$, $3.75$, $7.5$, $11.25$, $15$, $18.75$, $22.5$, $26.25$ and $30$Hz.
-So that, the package sampled in $15$hz was divided in $L=2$ frequency bands, 
-in $30$hz was divided in $L=4$ frequency bands, 
-in $45$hz was divided in $L=6$ frequency bands and finally
-in $60$hz was divided in $L=8$ frequency bands.
+In the other columns, we can see the results of $8$ frequency bands of package $P$,
+%these bands are 
+represented in the first line of table, with $l$, that indicates the position of frequency band
+in crescent order, relative to its frequency components, 
+%Thus, we have these frequency bands limited on: 
+with limits assigned at the frequencies: $0$, $3.75$, $7.5$, $11.25$, $15$, $18.75$, $22.5$, $26.25$ and $30$Hz;
+as can be seen in the second line of table.
+So that, the package sampled at $15$hz was divided in $L=2$ frequency bands, 
+the package sampled at $30$hz was divided in $L=4$ frequency bands, 
+the package sampled at $45$hz was divided in $L=6$ frequency bands and finally
+the package sampled at $60$hz was divided in $L=8$ frequency bands.
 
 The matrices $STDB$ are represented using a color palette, 
-that goes from dark blue to dark red color, representing of ascendant way the values
-in each pixel in all matrices. It is evident how the index values decreases with
-the increment of frequency sampling $F_s$ in each one of 8 frequency bands, 
-the index values also decrease with the increment of the position of frequency band,
-being the best analysis case, 
-in the sense of differentiating better places of lower and higher index, 
-to a frequency sampling of $15$ hz and a frequency band between $0$ Hz and $3.75$ Hz.
+that goes from dark blue (low values) to dark red color (high values), 
+%representing of ascendant way 
+linked to the values of activity,
+%in each pixel in all matrices, as It is shown in the top of table. 
+it is evident how the index values decreases with
+the increment of frequency sampling $F_s$.
+%in each one of 8 frequency bands, 
+The index values also decrease with the increment of the position of frequency band,
+being  a frequency band between $0$ Hz and $3.75$ Hz with a sampling rate of $15$ hz,
+the better analysis's case; in the sense of better differentiating places of lower and higher index value.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Analysis results} 
+\section{Discussions} 
 \label{sec:analysisresults}
 
-In the results seen in Section \ref{sec:numericalresults},
-we can observe in the Figure \ref{fig:MEANtest1} and \ref{fig:MEANtest2}, 
-that the indexes show a relation between the value of curve and the sampling frequency of datapack. 
-How is known \cite{Nothdurft:05}, the temporal speckle mean index is related to 
-the observed illumination level in the surface of study material and correspond to zero frequency of the signal (datapack).
+%In the results seen in Section \ref{sec:numericalresults}, we can observe in 
+In the Figure \ref{fig:MEANtest1} and \ref{fig:MEANtest2}, 
+%that 
+the indexes show a relation between the profile of mean index curve and the sampling frequency of datapack. 
+%How is known \cite{Nothdurft:05}, 
+The temporal speckle mean index (Fig. \ref{fig:MEANtest1}) is related to 
+the observed illumination level in the surface of the material \cite{Nothdurft:05} and  
+correspond to the analysis of zero frequency components of signal.
+%correspond to the offset in the frequency domain or frequency zero.
+%zero frequency of the signal (datapack);
 Thus, we can conclude that the level of illumination, perceived by the camera, 
-decrease with the increment of sampling frequency. 
-This is because that the exposition time is modified with the alteration of sampling frequency, 
-see Section \ref{subsec:expositiontime}, 
+decrease with the increment of sampling rate. 
+This is because that the exposition time is modified with the alteration of sampling frequency to commercial cameras, 
+%see Section \ref{subsec:expositiontime}, 
 so that less lighting is used to take the picture and consequently the 
-temporal speckle mean index decrease in  your value.
-In this sense, It is important have careful in to choose a sampling frequency
-that give us an index value superior to noise level of test or the quantization level of the camera.
+temporal speckle mean index decrease in  its value.
+In this sense, it is important to be aware to choose a sampling frequency
+that gives us an index value superior to the noise level of test or to the quantization level of the camera.
 
-The modification of exposition time also affect  and limit other indexes,
+The modification of exposition time also affects  and limits other indexes,
 remember that we have a quantization level between $0$ and $255$ in the camera. 
 We can see this interference in the Figures \ref{fig:AVDtest1}, \ref{fig:STDtest1}, \ref{fig:STDFtest1} and \ref{fig:INDEXtest2}, 
-where the $AVD(t)$, $STD(t)$ and $STDF(t)$ indexes decrease your values in concordance with the decrease of exposition time.
-Other way in that  the sampling frequency affect the values of indexes,
-It is that, it limits the frequency band of analyzed signal; for example,
+where the $AVD(t)$, $STD(t)$ and $STDF(t)$ indexes decrease their values in concordance with the decrease of exposition time.
+Other way in that  the sampling frequency affects the values of indexes,
+can be seen in the limitation of
+%It is that, it limits 
+the frequency band of an analyzed signal; for example,
 a sampling frequency $F_s$, by the Nyquist theorem \cite{Nyquist,Shannon}, 
-causes that the frequency band of analyzed signal (datapack)  will be between $0 Hz$ and $F_s/2~Hz$.
+causes  the limitation of  frequency band %of analyzed signal (datapack)  will be 
+between $0 Hz$ and $F_s/2~Hz$.
 Thus, in this context we have an index as $STD(t)$ that uses information between $\langle \left. 0, F_s/2 \right ] Hz$, 
-and be other side we have indexes as the $AVD(t)$ and the $STDF(t)$ index, that use information of half frequency band, 
-this is between $\left [ F_s/4, F_s/2 \right ] Hz$.
+while other  indexes as the $AVD(t)$ and the $STDF(t)$ index, use information of half frequency band, 
+between $\left [ F_s/4, F_s/2 \right ] Hz$.
 In the comparison between $STD(t)$ vs  $\{$ $STDF(t)$ and $AVD(t)$ $\}$, 
 we can see how the use of half, of entire frequency band, causes the decrease in the values of the curves, 
-but give us considerably good values in the maximum excursion of the curve. By other side,
-in the case of ink drying process, the use of complete frequency band, 
-It returns low values of maximum excursion in the curves. 
-The importance of excursion in this test,
- It is due the necessity of to have significant differences en the values of two states,
-when the sample start or end the ink drying process.
+but give us considerably good values in the maximum excursion of the curve across the time. By other side,
+in the case of ink drying process, the use of complete frequency band ($STD(t)$ index), 
+it returns low values of maximum excursion in the curves across the time. 
+The importance of excursion, in this test,
+ is due to the need of significant differences between the values of two states,
+during the
+%when the sample start or end the ink 
+drying process.
 
-It is necessary to highlight the importance of to choose the least value of sampling frequency $F_s$;
+It is necessary to highlight the importance of to choose the best value of sampling rate $F_s$;
 so that, 
-the frequency band of signal contain the frequency components with the information that you want to analyze;
-so that, the values of indexes have the greatest values and consequently a good excursion, 
-when compared with an inert part of sample; 
-By example, in the Table. \ref{table:2} is analyzed a corn seed, 
-we can see as the major values of indexes are obtained to a $F_s=15$ Hz, 
-analyzing frequency component between $0$ hz and $7.5$ Hz. At this point,
-an additionally result is evident, when we ask ourselves, 
-What is the best frequency band? where according with the test, we see that for
-all frequency bands, 
-the best frequency band, to the case of corn seed, is the one with the components with less frequency.
+the frequency band of a signal contain the frequency components with the information that you want to analyze;
+so that, the values of indexes have the greatest values and probably a good excursion, 
+when compared with an inert part of  the sample. 
+By example, in the Table. \ref{table:2}, it is analyzed a corn seed, 
+where we can see  the major values of indexes are obtained 
+from $0$ Hz and $7.5$ Hz, when $F_s=15$ Hz.
+
+Thus, at this point,
+an question is evident: 
+What is the best frequency band? According with the test of corn seed, 
+we see that for all frequency bands, 
+the best range, 
+is the one with the components with lowest possible frequencies; 
+but without forget that given a $STD(t)$ analysis, 
+this index extract information of inner parts of material \cite{Nothdurft:05}, 
+and this information decrease jointly with the decrease of frequency band,
+as can be seen when compared the result in the excursion of $STD(t)$, 
+with frequency components in low frequencies,
+and the excursion of $\{$ $STDF(t)$ and $AVD(t)$ $\}$, 
+with frequency components in high frequencies;
+so that we need to choose a compromise between the desired quantity of inner information in the sample, 
+the perceived illumination level and the sampling rate.
 
@@
 
-In this work were presented comparisons of behavior of three dynamic speckle indexes
-subject to different values of sampling frequency, thus we concluded that:
-It is important to know to choose an appropriate sampling frequency, 
+In this work were presented comparisons of three dynamic laser speckle indexes,
+subject to different values of sampling rate.
+thus we conclude that it is important to choose an appropriate sampling rate, 
 being recommendable to use the minimal sampling frequency possible to get an acceptable maximum excursion, 
-so that the phenomenon under study to be in the analyzed frequency band.
-Finally, 
-we show that the digitization  of speckle signal imply a restriction of frequency 
+in index as the $AVD$ and $STDF$,
+and an illumination level in the images with good signal-noise relation,
+so that the phenomenon under study can be collected in the chosen analysis frequency band.
+We showed that the digitization  of speckle signal imply a restriction of frequency 
 band of signal and consequently this affect the result of an speckle analysis.
+And the user of a digital camera must be aware that the increase of the frame rate (fps) 
+force the commercial cameras to change the perceived illumination level in the camera sensor.
 

### 2019-09-06 article/article_1.tex
pronto para submeter

@@
 
-\journal{Optics Communications}
+\journal{Optics and Lasers in Engineering}
 
@@
 
-\title{Sampling Frequency in the Dynamic Speckle Analysis}
+\title{Sampling Rate in the Dynamic Speckle Analysis}
 %\tnotetext[mytitlenote]{Fully documented templates are available in the 
@@
 % Group authors per affiliation:
-\author{Rivera, F. P.}
-\author{Pe\~na, R. G.}
+\author{Pujaico~Rivera, F.}
+\author{Gonzalez-Pe\~na, R. J.}
 \author{Braga, R. A.}
@@
 \begin{abstract}
-In this article, we show as the variation of sampling frequency, 
-in a dynamic speckle analysis, affects the value of some dynamic speckle index, 
-to the cases of the absolute value of the differences index, the temporal 
-speckle standard deviation index and the temporal 
-speckle mean index.
-We show that  the dynamic speckle index value change the maximum excursion with 
-the variation of sampling frequency, affected directly by the time integration 
+In this article, we show as the variation of sampling rate, 
+in a dynamic speckle analysis, affects the value of some dynamic speckle indexes, 
+to the cases of the absolute value of the differences index, 
+the temporal speckle standard deviation index and the temporal speckle mean index.
+We show that  the dynamic speckle index value changes its maximum excursion with 
+the variation of sampling rate, affected directly by the time integration 
 (exposition time) of camera.
 We highlight the importance of knowing  the frequency band of analyzed phenomenon, 
-in order to choose the appropriate sampling frequency, 
-being recommendable to use the minimal sampling frequency possible
+in order to choose the appropriate sampling rate, 
+being recommendable to use the minimal sampling rate possible
 to get an acceptable maximum excursion, 
@@
 \begin{keyword}
-Sampling frequency \sep
+Sampling rate \sep
 Dynamic speckle index \sep 
@@
 in these sense,
-we analyze the effect of sampling frequency, 
+we analyze the effect of sampling rate, 
 and consequently the time exposure, in a dynamic laser speckle analysis
@@
 %4) Relevancia do artigo(importancia para outros del artigo publicado)
-Knowing the effect of sampling frequency over an index value,
-a researcher will be able to have a criteria to choose the appropriate sampling frequency 
+Knowing the effect of sampling rate over an index value,
+a researcher will be able to have a criteria to choose the appropriate sampling rate
 for a certain monitored phenomenon. 
@@
 For this purpose, we show that given a dynamic speckle test, exists an appropriate frequency band
-to the sampling frequency. High values of sampling rate may cause unintended consequences on the index value, 
+to the sampling rate. High values of sampling rate may cause unintended consequences on the index value, 
 such as the decrease of the excursion between two activity levels, given a determinate index value. 
-In turn, decreasing the sampling frequency promoted by the increasing of the exposure time,
+In turn, decreasing the sampling rate promoted by the increasing of the exposure time,
 will cause a reduction of the temporal speckle contrast,
@@
 \label{subsec:expositiontime}
-The sampling frequency ($F_s$) or acquisition time in frames per second ($fps$), 
+The sampling rate ($F_s$) or acquisition time in frames per second ($fps$), 
 in the camera Marlin F-033 is obtained using the 
@@
 \end{tabular}
-\caption{Exposition time and sampling frequency}
+\caption{Exposition time and sampling rate}
 \label{table:1}
@@
 band ($0$ until $F_s/2$ Hz), as seen in Section \ref{sec:std}.
-This index shows a different behavior in time to each sampling frequency,
+This index shows a different behavior in time to each sampling rate,
 so that, the value of the index in each time  decreases in proportion with 
@@
 it can be seen that exists a considerable difference between the maximum excursion 
-of the curves with the use of sampling frequency; so, it is possible to observe a 
+of the curves with the use of sampling rate; so, it is possible to observe a 
 grow of the maximum excursion when the sampling rate decrease, like the $AVD(t)$ index.
@@
 %We observe as the index decrease your value, 
-with the increment of sampling frequency, %in the datapack,
+with the increment of sampling rate, %in the datapack,
 where from %so that between 
@@
 it is evident how the index values decreases with
-the increment of frequency sampling $F_s$.
+the increment of sampling rate $F_s$.
 %in each one of 8 frequency bands, 
@@
 %that 
-the indexes show a relation between the profile of mean index curve and the sampling frequency of datapack. 
+the indexes show a relation between the profile of mean index curve and the sampling rate of datapack. 
 %How is known \cite{Nothdurft:05}, 
@@
 temporal speckle mean index decrease in  its value.
-In this sense, it is important to be aware to choose a sampling frequency
+In this sense, it is important to be aware to choose a sampling rate
 that gives us an index value superior to the noise level of test or to the quantization level of the camera.
@@
 where the $AVD(t)$, $STD(t)$ and $STDF(t)$ indexes decrease their values in concordance with the decrease of exposition time.
-Other way in that  the sampling frequency affects the values of indexes,
+Other way in that  the sampling rate affects the values of indexes,
 can be seen in the limitation of
@@
 the frequency band of an analyzed signal; for example,
-a sampling frequency $F_s$, by the Nyquist theorem \cite{Nyquist,Shannon}, 
+a sampling rate $F_s$, by the Nyquist theorem \cite{Nyquist,Shannon}, 
 causes  the limitation of  frequency band %of analyzed signal (datapack)  will be 
@@
 Thus, at this point,
-an question is evident: 
+a question is evident: 
 What is the best frequency band? According with the test of corn seed, 
 we see that for all frequency bands, 
-the best range, 
-is the one with the components with lowest possible frequencies; 
+the best range is the one with the components with lowest frequencies; 
 but without forget that given a $STD(t)$ analysis, 
 this index extract information of inner parts of material \cite{Nothdurft:05}, 
-and this information decrease jointly with the decrease of frequency band,
+and this information decreases jointly with the decrease of frequency band,
 as can be seen when compared the result in the excursion of $STD(t)$, 
-with frequency components in low frequencies,
-and the excursion of $\{$ $STDF(t)$ and $AVD(t)$ $\}$, 
-with frequency components in high frequencies;
+with components in low frequencies,
+and the excursion of \{$STDF(t)$ and $AVD(t)$\}, 
+with components in high frequencies;
 so that we need to choose a compromise between the desired quantity of inner information in the sample, 
@@
 thus we conclude that it is important to choose an appropriate sampling rate, 
-being recommendable to use the minimal sampling frequency possible to get an acceptable maximum excursion, 
+being recommendable to use the minimal sampling rate possible to get an acceptable maximum excursion, 
 in index as the $AVD$ and $STDF$,
